---
title: "Distribution"
author: "Panther"
date: "February 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Load Data

```{r Load Data, message=FALSE}
library(quanteda); library(tidyverse); library(TTR);library(ggplot2);library(scales); library(fOptions); library(pastecs); library(psych);library(crayon);library(PerformanceAnalytics);library(stats);library(RQuantLib);

# here data read is being processed
#t <- read_csv("../data/data_div.csv")
#t <- read_csv("../Data/data.csv")
t <- read_csv("F:/Dropbox/[IAQF]/Data/data_final.csv")
t <- t[-1,]  #dump first day NA

# t$Date <- strptime(as.character(t$Date), "%m/%d/%Y")
# format(t$Date, "%Y-%m-%d")
# t$Date <- as.Date(t$Date)

```


#Plot SPC and moving average

```{r Plot index and moving average}

t$POSIXct_Date <- as.POSIXct(t$Date)

ggplot(t,aes(x=POSIXct_Date)) + 
  geom_line(aes(y=Close,color="Close")) +
  geom_line(aes(y=SMA60,color="SMA60")) +
  geom_line(aes(y=SMA120,color="SMA120"))+ 
  scale_x_datetime(breaks=date_breaks("1 year"),labels = date_format("%y")) +
  labs(color="Legend")+
  scale_colour_manual("", breaks = c("Close", "SMA60","SMA120"),
                          values = c("blue", "red","green")) +
  ggtitle("Closing index and moving averge for all data")

a = 4500
c = 7069

ggplot(t[a:c,],aes(x=POSIXct_Date)) + 
  geom_line(aes(y=Close,color="Close")) +
  geom_line(aes(y=SMA60,color="SMA60")) +
  geom_line(aes(y=SMA120,color="SMA120"))+ 
  scale_x_datetime(breaks=date_breaks("1 year"),labels = date_format("%y")) +
  labs(color="Legend")+
  scale_colour_manual("", breaks = c("Close", "SMA60","SMA120"),
                          values = c("blue", "red","green")) +
  ggtitle("Closing index and moving averge for 10 years")

```


#Momentum effect of portfolio returns
Obvious autocorrelation, large ARMA parameters

```{r Momentum effect}

acf(t$port1_Relreturn,lag.max = 20,type='correlation')
pacf(t$port1_Relreturn,lag.max = 50)

acf(t$port2_Relreturn,lag.max = 20,type='correlation')
pacf(t$port2_Relreturn,lag.max = 50)

acf(t$port3_Relreturn,lag.max = 20,type='correlation')
pacf(t$port3_Relreturn,lag.max = 50)

acf(t$port4_Relreturn,lag.max = 20,type='correlation')
pacf(t$port4_Relreturn,lag.max = 50)

```



# Scatter of RelReturn

```{r Scatter Plot RelReturn}

ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port1_Relreturn),size =1, shape= 1)

ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port2_Relreturn),size =1, shape= 1)


ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port3_Relreturn),size =1, shape= 1)

ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port4_Relreturn),size =1, shape= 1) 
#  ylim(-250000,350000)

ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port1_Relreturn,color="Port1"),alpha=0.2) +
  geom_point(aes(y=port2_Relreturn,color="Port2"),alpha=0.2) +
  geom_point(aes(y=port3_Relreturn,color="Port3"),alpha=0.2) +
  geom_point(aes(y=port4_Relreturn,color="Port4"),alpha=0.2) +
  ylim(-100000,200000) +
  theme_bw() +
  ggtitle("Relreturn comparing for four portfolios")

```


#Histogram of RelReturn
Portfolio 2 is strongly non-central and skewed
Portfolio 4 is pretty discrete

```{r Histogram Plot RelReturn}

ggplot(t,aes(x = port1_Relreturn)) + 
  geom_histogram(aes(y=..density..,fill=..count..)) +
  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port1_Relreturn),sd = sd(t$port1_Relreturn))) +
  theme_bw()

ggplot(t,aes(x = port2_Relreturn)) + 
  geom_histogram(aes(y=..density..,fill=..count..)) +
  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port2_Relreturn),sd = sd(t$port2_Relreturn))) +
  theme_bw()

ggplot(t,aes(x = port3_Relreturn)) + 
  geom_histogram(aes(y=..density..,fill=..count..)) +
  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port3_Relreturn),sd = sd(t$port3_Relreturn))) +
  theme_bw()

ggplot(t,aes(x = port4_Relreturn)) + 
  geom_histogram(aes(binwidth = 1,y=..density..,fill=..count..)) +
  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port4_Relreturn),sd = sd(t$port4_Relreturn))) +
#  xlim(-10000,10000) +
  theme_bw()



```



#QQ plot of Relreturn

```{r QQ Plot Relreturn}

ggplot(t, aes(sample=port1_Relreturn)) +  stat_qq() 
ggplot(t, aes(sample=port2_Relreturn)) +  stat_qq() 
ggplot(t, aes(sample=port3_Relreturn)) +  stat_qq() 
ggplot(t, aes(sample=port4_Relreturn)) +  stat_qq() 


```


#Statistics of Relreturn

```{r Statistics of Relreturn}

cat(red("Relreturn Statistics in all time\n"))
cat(blue("Portfolio 1\n"))
stat.desc(t$port1_Relreturn)
describe(t$port1_Relreturn)

cat(blue("Portfolio 2\n"))
stat.desc(t$port2_Relreturn)
describe(t$port2_Relreturn)

cat(blue("Portfolio 3\n"))
stat.desc(t$port3_Relreturn)
describe(t$port3_Relreturn)

cat(blue("Portfolio 4\n"))
stat.desc(t$port4_Relreturn)
describe(t$port4_Relreturn)


```



#Statistics Comparison

```{r Statistics table}

base <- t[,c(11,13,15,17)]
colnames(base) <- c("port1_Relreturn","port2_Relreturn","port3_Relreturn","port4_Relreturn")

#base <- t[,c(9,11,13,15)]
#colnames(base) <- c("port1_absreturn","port2_absreturn","port3_absreturn","port4_absreturn")

stat <- sapply(base,sum) %>%
  rbind(sapply(base,mean)) %>%
  rbind(sapply(base,mean)*252) %>%
  rbind(sapply(base,var)) %>%
  rbind(sapply(base,skew)) %>%
  rbind(sapply(base,kurtosis))

rownames(stat) <- c("sum","mean","annual mean","var","skew","kurtosis")

print("Statistics in all time")
print(stat)


```

#Cumulative RelReturn
See how the cost of options and straddles ruined your return


```{r Cumulative Relreturn}

t$port1_cum_Relreturn <- cumsum(t$port1_Relreturn)
t$port2_cum_Relreturn <- cumsum(t$port2_Relreturn)
t$port3_cum_Relreturn <- cumsum(t$port3_Relreturn)
t$port4_cum_Relreturn <- cumsum(t$port4_Relreturn)

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_cum_Relreturn,color="Port1")) +
  geom_line(aes(y=port2_cum_Relreturn,color="Port2")) +
  geom_line(aes(y=port3_cum_Relreturn,color="Port3")) +
  geom_line(aes(y=port4_cum_Relreturn,color="Port4")) +
#  ylim(-10000000,50000000) +
  theme_bw() +
  ggtitle("Cumulative Return comparing in all time")


```


#Realized Volatility on Relreturn
Realized Vol is limited, 10 years has upper boundary


```{r Realized Volatility}

t$port1_real_vol <- 252*cumsum(t$port1_Relreturn^2)/seq(length(t$port1_Relreturn)) %>% sqrt()
t$port2_real_vol <- 252*cumsum(t$port2_Relreturn^2)/seq(length(t$port2_Relreturn)) %>% sqrt()
t$port3_real_vol <- 252*cumsum(t$port3_Relreturn^2)/seq(length(t$port3_Relreturn)) %>% sqrt()
t$port4_real_vol <- 252*cumsum(t$port4_Relreturn^2)/seq(length(t$port4_Relreturn)) %>% sqrt()

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_real_vol,color="Port1")) +
  geom_line(aes(y=port2_real_vol,color="Port2")) +
  geom_line(aes(y=port3_real_vol,color="Port3")) +
  geom_line(aes(y=port4_real_vol,color="Port4")) +
#  ylim(-1000,10000) +
  theme_bw() +
  ggtitle("Realized Volatility in all time")

```


#Rolling Analysis annually(252 days)
Rolling mean is smoother, bur going worse. 
Rolling vlo is controlled. 
Rolling correlation is towards positive, which is not we expecting.


```{r Rolling Analysis annually}

port1 <- xts(x=t$port1_Relreturn, order.by=t$Date)
port2 <- xts(x=t$port2_Relreturn, order.by=t$Date)
port3 <- xts(x=t$port3_Relreturn, order.by=t$Date)
port4 <- xts(x=t$port4_Relreturn, order.by=t$Date)

t$port1_roll_mean <- apply.rolling(port1,252,gap=252,by=1,FUN="mean")
t$port2_roll_mean <- apply.rolling(port2,252,gap=252,by=1,FUN="mean")
t$port3_roll_mean <- apply.rolling(port3,252,gap=252,by=1,FUN="mean")
t$port4_roll_mean <- apply.rolling(port4,252,gap=252,by=1,FUN="mean")

t$port1_roll_vol <- apply.rolling(port1,252,gap=252,by=1,FUN="sd")
t$port2_roll_vol <- apply.rolling(port2,252,gap=252,by=1,FUN="sd")
t$port3_roll_vol <- apply.rolling(port3,252,gap=252,by=1,FUN="sd")
t$port4_roll_vol <- apply.rolling(port4,252,gap=252,by=1,FUN="sd")


ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_roll_mean,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_roll_mean,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port3_roll_mean,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port4_roll_mean,na.rm = TRUE)) 

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_roll_vol,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_roll_vol,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port3_roll_vol,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port4_roll_vol,na.rm = TRUE))

chart.RollingCorrelation(t$port1_roll_mean, t$port1_roll_vol,252)
chart.RollingCorrelation(t$port2_roll_mean, t$port2_roll_vol,252)
chart.RollingCorrelation(t$port3_roll_mean, t$port3_roll_vol,252)
chart.RollingCorrelation(t$port4_roll_mean, t$port4_roll_vol,252)

```

#Rolling Analysis 60 days
Rolling mean is smoother, bur going worse. 
Rolling vlo is controlled. 
Rolling correlation is towards positive, which is not we expecting.

```{r Rolling Analysis 60 days}

port1 <- xts(x=t$port1_Relreturn, order.by=t$Date)
t$port1_roll_mean <- apply.rolling(port1,60,gap=60,by=1,FUN="mean")
t$port1_roll_vol <- apply.rolling(port1,60,gap=60,by=1,FUN="sd")
port2 <- xts(x=t$port2_Relreturn, order.by=t$Date)
t$port2_roll_mean <- apply.rolling(port2,60,gap=60,by=1,FUN="mean")
t$port2_roll_vol <- apply.rolling(port2,60,gap=60,by=1,FUN="sd")
port3 <- xts(x=t$port3_Relreturn, order.by=t$Date)
t$port3_roll_mean <- apply.rolling(port3,60,gap=60,by=1,FUN="mean")
t$port3_roll_vol <- apply.rolling(port3,60,gap=60,by=1,FUN="sd")
port4 <- xts(x=t$port4_Relreturn, order.by=t$Date)
t$port4_roll_mean <- apply.rolling(port4,60,gap=60,by=1,FUN="mean")
t$port4_roll_vol <- apply.rolling(port4,60,gap=60,by=1,FUN="sd")

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_roll_mean,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_roll_mean,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port3_roll_mean,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port4_roll_mean,na.rm = TRUE)) 


ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_roll_vol,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_roll_vol,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port3_roll_vol,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port4_roll_vol,na.rm = TRUE))


chart.RollingCorrelation(t$port1_roll_mean, t$port1_roll_vol,60)
chart.RollingCorrelation(t$port2_roll_mean, t$port2_roll_vol,60)
chart.RollingCorrelation(t$port3_roll_mean, t$port3_roll_vol,60)
chart.RollingCorrelation(t$port4_roll_mean, t$port4_roll_vol,60)


```






setwd("F:/Dropbox/[IAQF_Max]/R")
write_csv(t,"../data/data.csv")


