---
title: "Exploration"
author: "Panther"
date: "Jan 28,2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Load Data

```{r Load Data, message=FALSE}
library(quanteda); library(tidyverse); library(TTR);library(ggplot2);library(scales); library(fOptions); library(pastecs); library(psych);library(crayon);library(PerformanceAnalytics);library(stats);library(RQuantLib);

# here data read is being processed
#t <- read_csv("../data/data_div.csv")
#t <- read_csv("../Data/data.csv")
t <- read_csv("F:/Dropbox/[IAQF]/Data/data.csv")
# t$Date <- strptime(as.character(t$Date), "%m/%d/%Y")
# format(t$Date, "%Y-%m-%d")
# t$Date <- as.Date(t$Date)

```

#Process Data

```{r Process Data}

GSPC <- read_csv("../data/^GSPC.csv")
LIBOR <- read_csv("../data/USD3MTD156N.csv")
Treasury <- read_csv("../data/DTB3.csv")
VIX <- read_csv("../data/^VIX.csv")

#t$newDate <- strptime(as.character(t$Date), "%m/%d/%Y")
#format(t$newDate, "%Y-%m-%d")
#t$Date <- as.Date(t$newDate)
#t <- t[-10]

t<-cbind(GSPC,Treasury$DTB3[match(GSPC$Date,Treasury$DATE)])
t<-cbind(t,VIX$Close[match(t$Date,VIX$Date)])
t<-t[,c(1,5,8,9)]
t<- t[-1:(-10054+120),]  # extra 120 for training signal, will remove later
colnames(t)[3] <- "Free_rate"
colnames(t)[4] <- "VIX"
t$Free_rate = as.numeric(as.character(t$Free_rate))


```

#Missing Data

```{r Missing Data}

sum(is.na(t))
sum(is.na(t$Close))
sum(is.na(t$Free_rate))
sum(is.na(t$VIX))

which(is.na(t$Free_rate))
#count(which(is.na(t$Free_rate)))

temp <- which(is.na(t$Free_rate))
for (i in temp)
  t$Free_rate[i] <- mean(t$Free_rate[(i-5):(i+5)], na.rm=TRUE)

sum(is.na(t$Free_rate))

```

#Moving Average and momentum signal

```{r momentum signal}

t$SMA60 <- SMA(t$Close,60)
t$SMA120 <- SMA(t$Close,120)
t<- t[-1:-120,]     # here remove training 120
for (i in seq_along(t$SMA120)){
  if (t$SMA60[i]>t$SMA120[i])
     t$signal[i] = 1            # signal = 1 is buy singal
  else if (t$SMA60[i]<t$SMA120[i])
     t$signal[i] = 0
  else
     t$signal[i] = t$singal[i-1]
}

```

#Plot SPC and moving average

```{r Plot index and moving average}

t$POSIXct_Date <- as.POSIXct(t$Date)

ggplot(t,aes(x=POSIXct_Date)) + 
  geom_line(aes(y=Close,color="Close")) +
  geom_line(aes(y=SMA60,color="SMA60")) +
  geom_line(aes(y=SMA120,color="SMA120"))+ 
  scale_x_datetime(breaks=date_breaks("1 year"),labels = date_format("%y")) +
  labs(color="Legend")+
  scale_colour_manual("", breaks = c("Close", "SMA60","SMA120"),
                          values = c("blue", "red","green")) +
  ggtitle("Closing index and moving averge for all data")

a = 4500
c = 7069

ggplot(t[a:c,],aes(x=POSIXct_Date)) + 
  geom_line(aes(y=Close,color="Close")) +
  geom_line(aes(y=SMA60,color="SMA60")) +
  geom_line(aes(y=SMA120,color="SMA120"))+ 
  scale_x_datetime(breaks=date_breaks("1 year"),labels = date_format("%y")) +
  labs(color="Legend")+
  scale_colour_manual("", breaks = c("Close", "SMA60","SMA120"),
                          values = c("blue", "red","green")) +
  ggtitle("Closing index and moving averge for 10 years")

```


## Create portfolios
Absolute Return = shift between one lag of close prices
Percentage Return = Absolute Return / last day close price
Relative Return = Percentage return * initiate price($100,000)
We use Relative Return as analysis object

#portfolio 1
Buy/short 1 index on today's closing and close position next day
Assume when you short today, you buy an index for paying back next day
Recieve dividend while buying

```{r portfolio 1}

#t$port1_absreturn[1] = NA
#t$port1_Perreturn[1] = NA
t$port1_Relreturn[1] = NA


for (i in seq_along(t$Close[1:(length(t$Close)-1)])){
  if (t$signal[i]== 1){
#     t$port1_absreturn[i+1] = t$Close[i+1]-t$Close[i]
#     t$port1_Perreturn[i+1] = (t$Close[i+1]-t$Close[i]) / t$Close[i]
     t$port1_Relreturn[i+1] = (t$Close[i+1]-t$Close[i]+t$Close[i]*t$DivYield[i]/365*as.numeric(difftime(t$Date[i+1],t$Date[i]))) / t$Close[i] * 100000
     }
  else{
#     t$port1_absreturn[i+1] = t$Close[i]-t$Close[i+1]
#     t$port1_Perreturn[i+1] = (t$Close[i]-t$Close[i+1]) / t$Close[i]
     t$port1_Relreturn[i+1] = (t$Close[i]-t$Close[i+1]) / t$Close[i] * 100000
     }
}

```

#portfolio 2
Buy at the money call/put option(90 days maturity) on today's closing and close position next day
Volatility is VIX
Risk free rate is 90 days T-bill rate
Consider dividends

```{r portfolio 2}

#t$port2_absreturn[1] = NA
#t$port2_Perreturn[1] = NA
t$port2_Relreturn[1] = NA

#if (t$signal[1] == 1) {
#  cc <- GBSOption("c",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))
#  } else {
#  cc <- GBSOption("p",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))

# for (i in seq_along(t$Close[1:(length(t$Close)-1)])){
#
#   if (t$signal[i]== 1){
#      aa <- GBSOption("c",t$Close[i+1],t$Close[i],(90-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365,(t$Free_rate[i+1]/100),0,(t$VIX[i+1]/100))
#      bb <- GBSOption("c",t$Close[i],t$Close[i],0.246575342,(t$Free_rate[i]/100),0,(t$VIX[i]/100))
#     } else{
#      aa <- GBSOption("p",t$Close[i+1],t$Close[i],(90-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365,(t$Free_rate[i+1]/100),0,(t$VIX[i+1]/100))
#      bb <- GBSOption("p",t$Close[i],t$Close[i],0.246575342,(t$Free_rate[i]/100),0,(t$VIX[i]/100))
#     }
#      t$port2_absreturn[i+1] = aa@price-bb@price
#      t$port2_Perreturn[i+1] = (aa@price-bb@price) / bb@price
# #     t$port2_Relreturn[i+1] = t$port2_Perreturn[i+1] * t$Close[1]
# }

for (i in seq_along(t$Close[1:(length(t$Close)-1)])){

  if (t$signal[i]== 1){
    aa <- EuropeanOption("call", t$Close[i+1], t$Close[i],t$DivYield[i+1], (t$Free_rate[i+1]/100), (90-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365, (t$VIX[i+1]/100))
    bb <- EuropeanOption("call", t$Close[i], t$Close[i],t$DivYield[i], (t$Free_rate[i]/100), 0.246575342, (t$VIX[i]/100))
    } else {
    aa <- EuropeanOption("put", t$Close[i+1], t$Close[i],t$DivYield[i+1], (t$Free_rate[i+1]/100), (90-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365, (t$VIX[i+1]/100))
    bb <- EuropeanOption("put", t$Close[i], t$Close[i],t$DivYield[i], (t$Free_rate[i]/100), 0.246575342, (t$VIX[i]/100))
  }
#     t$port2_absreturn[i+1] = aa$value-bb$value
#     t$port2_Perreturn[i+1] = (aa$value-bb$value) / bb$value
     t$port2_Relreturn[i+1] = (aa$value-bb$value) / bb$value * 100000
}

```


#portfolio 3
Buy at the money straddle(90 days maturity) on today's closing and close position next day
Volatility is VIX
Risk free rate is 90 days T-bill rate
Consider dividends


```{r portfolio 3}

#t$port3_absreturn[1] = NA
#t$port3_Perreturn[1] = NA
t$port3_Relreturn[1] = NA

#ca <- GBSOption("c",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))
#cb <- GBSOption("p",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))
#cc = ca@price + cb@price

for (i in seq_along(t$Close[1:(length(t$Close)-1)])){
    aa1 <- EuropeanOption("call", t$Close[i+1], t$Close[i],t$DivYield[i+1], (t$Free_rate[i+1]/100), (90-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365, (t$VIX[i+1]/100))
    aa2 <- EuropeanOption("put", t$Close[i+1], t$Close[i],t$DivYield[i+1], (t$Free_rate[i+1]/100), (90-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365, (t$VIX[i+1]/100))
    bb1 <- EuropeanOption("call", t$Close[i], t$Close[i],t$DivYield[i], (t$Free_rate[i]/100), 0.246575342, (t$VIX[i]/100))
    bb2 <- EuropeanOption("put", t$Close[i], t$Close[i],t$DivYield[i], (t$Free_rate[i]/100), 0.246575342, (t$VIX[i]/100))

#    t$port3_absreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value)
#    t$port3_Perreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value) / (bb1$value+bb2$value)
    t$port3_Relreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value) / (bb1$value+bb2$value)*100000
}

```

#portfolio 4
Buy at the money straddle(90 days maturity but remain life decrease until rebalance at maturity)
- on today's closing and close position next day
Volatility is VIX
Risk free rate is 90 days T-bill rate
Consider dividends

```{r portfolio 4}

#t$port4_absreturn[1] = NA
#t$port4_Perreturn[1] = NA
t$port4_Relreturn[1] = NA

#ca <- GBSOption("c",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))
#cb <- GBSOption("p",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))
#cc = ca@price + cb@price

#date.lookup <- format(seq(as.Date("2000-01-02"), as.Date("2018-1-19"), by = "1 day"))
#date.except <- subset(b, !(y %in% a$x))
#match("2024-01-19", date.lookup)

count=0   #count days passed

for (i in seq_along(t$Close[1:(length(t$Close)-1)])){

  if (as.numeric(difftime(t$Date[i+1],t$Date[i])) == 1){   #workday
    count = count+1}
  else {                                            # not workday
    count = count+as.numeric(difftime(t$Date[i+1],t$Date[i])) }

  if (count <= 89){
    Remaina = 90 - count         # today's remain
    Remainb = Remaina + 1}        # previous day's remain
  else if (count >= 90) {       # expired already, adjuste to 90 days passed
    Remaina = 0                 # today's remain
    Remainb = 1                 # previous day's remain
    count = 0 }                 # after expired, rebalance

  aa1 <- EuropeanOption("call", t$Close[i+1], t$Close[i],t$DivYield[i+1], (t$Free_rate[i+1]/100), 0.246575342*Remaina/90, (t$VIX[i+1]/100),0, 0)
  aa2 <- EuropeanOption("put", t$Close[i+1], t$Close[i],t$DivYield[i+1], (t$Free_rate[i+1]/100), 0.246575342*Remaina/90, (t$VIX[i+1]/100),0, 0)
  bb1 <- EuropeanOption("call", t$Close[i], t$Close[i],t$DivYield[i], (t$Free_rate[i]/100), 0.246575342*Remainb/90, (t$VIX[i]/100),0, 0)
  bb2 <- EuropeanOption("put", t$Close[i], t$Close[i],t$DivYield[i], (t$Free_rate[i]/100), 0.246575342*Remainb/90, (t$VIX[i]/100),0, 0)


#  t$port4_absreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value)
#  t$port4_Perreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value) / (bb1$value+bb2$value)
  t$port4_Relreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value) / (bb1$value+bb2$value)*100000
}

```


#Dump first day NA return
```{r}
t <- t[-1,]
```

#Momentum effect of portfolio returns
Obvious autocorrelation, large ARMA parameters

```{r Momentum effect}

acf(t$port1_Relreturn,lag.max = 20,type='correlation')
pacf(t$port1_Relreturn,lag.max = 50)

acf(t$port2_Relreturn,lag.max = 20,type='correlation')
pacf(t$port2_Relreturn,lag.max = 50)

acf(t$port3_Relreturn,lag.max = 20,type='correlation')
pacf(t$port3_Relreturn,lag.max = 50)

acf(t$port4_Relreturn,lag.max = 20,type='correlation')
pacf(t$port4_Relreturn,lag.max = 50)

```



#Line Plot Absolute Return

```{r Line Plot Absolute Return}

#ggplot(t,aes(x=Date)) + 
#  geom_line(aes(y=port1_absreturn))

#ggplot(t,aes(x=Date)) + 
#  geom_line(aes(y=port2_absreturn))

#ggplot(t,aes(x=Date)) + 
#  geom_line(aes(y=port3_absreturn))

#ggplot(t,aes(x=Date)) + 
#  geom_line(aes(y=port4_absreturn))


```

#Line Plot Percentage Return

```{r Line Plot Percentage Return}

#ggplot(t,aes(x=Date)) + 
#  geom_line(aes(y=port1_Perreturn))

#ggplot(t,aes(x=Date)) + 
#  geom_line(aes(y=port2_Perreturn))

#ggplot(t,aes(x=Date)) + 
#  geom_line(aes(y=port3_Perreturn))

#ggplot(t,aes(x=Date)) + 
#  geom_line(aes(y=port4_Perreturn))


```


# Scatter of RelReturn

```{r Scatter Plot RelReturn}

ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port1_Relreturn),size =1, shape= 1)

ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port2_Relreturn),size =1, shape= 1)


ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port3_Relreturn),size =1, shape= 1)

ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port4_Relreturn),size =1, shape= 1) 
#  ylim(-250000,350000)

ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port1_Relreturn,color="Port1"),alpha=0.2) +
  geom_point(aes(y=port2_Relreturn,color="Port2"),alpha=0.2) +
  geom_point(aes(y=port3_Relreturn,color="Port3"),alpha=0.2) +
  geom_point(aes(y=port4_Relreturn,color="Port4"),alpha=0.2) +
  ylim(-100000,200000) +
  theme_bw() +
  ggtitle("Relreturn comparing for four portfolios")

#a = 4500
#c = 7068

#ggplot(t[a:c,],aes(x=Date)) + 
#  geom_point(aes(y=port1_absreturn,color="Port1"),alpha=0.5,shape= 1) +
#  geom_point(aes(y=port2_absreturn,color="Port2"),alpha=0.5,shape= 0) +
#  geom_point(aes(y=port3_absreturn,color="Port3"),alpha=0.5,shape= 2) +
#  geom_point(aes(y=port4_absreturn,color="Port4"),alpha=0.5,shape= 5) +
#  theme_bw() +
#  ggtitle("absreturn Return comparing for four portfolios in 10 years")

```

# Scatter of Percentage Return

```{r Scatter Plot Percentage Return}

ggplot(t,aes(x=Date)) +
  geom_point(aes(y=port1_Perreturn),size =1, shape= 1)

ggplot(t,aes(x=Date)) +
  geom_point(aes(y=port2_Perreturn),size =1, shape= 1)

ggplot(t,aes(x=Date)) +
  geom_point(aes(y=port3_Perreturn),size =1, shape= 1)

ggplot(t,aes(x=Date)) +
  geom_point(aes(y=port4_Perreturn),size =1, shape= 1)

ggplot(t,aes(x=Date)) +
  geom_point(aes(y=port1_Perreturn,color="Port1"),alpha=0.2) +
  geom_point(aes(y=port2_Perreturn,color="Port2"),alpha=0.2) +
  geom_point(aes(y=port3_Perreturn,color="Port3"),alpha=0.2) +
  geom_point(aes(y=port4_Perreturn,color="Port4"),alpha=0.2) +
  theme_bw() +
  ggtitle("percentage Return comparing for four portfolios")

#a = 4500
#c = 7068

#ggplot(t[a:c,],aes(x=Date)) +
#  geom_point(aes(y=port1_Perreturn,color="Port1"),alpha=0.5,shape= 1) +
#  geom_point(aes(y=port2_Perreturn,color="Port2"),alpha=0.5,shape= 0) +
#  geom_point(aes(y=port3_Perreturn,color="Port3"),alpha=0.5,shape= 2) +
#  geom_point(aes(y=port4_Perreturn,color="Port4"),alpha=0.5,shape= 5) +
#  theme_bw() +
#  ggtitle("percentage Return comparing for four portfolios in 10 years")

```

#Histogram of RelReturn
Portfolio 2 is strongly non-central and skewed
Portfolio 4 is pretty discrete

```{r Histogram Plot RelReturn}

ggplot(t,aes(x = port1_Relreturn)) + 
  geom_histogram(aes(y=..density..,fill=..count..)) +
  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port1_Relreturn),sd = sd(t$port1_Relreturn))) +
  theme_bw()

ggplot(t,aes(x = port2_Relreturn)) + 
  geom_histogram(aes(y=..density..,fill=..count..)) +
  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port2_Relreturn),sd = sd(t$port2_Relreturn))) +
  theme_bw()

ggplot(t,aes(x = port3_Relreturn)) + 
  geom_histogram(aes(y=..density..,fill=..count..)) +
  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port3_Relreturn),sd = sd(t$port3_Relreturn))) +
  theme_bw()

ggplot(t,aes(x = port4_Relreturn)) + 
  geom_histogram(aes(binwidth = 1,y=..density..,fill=..count..)) +
  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port4_Relreturn),sd = sd(t$port4_Relreturn))) +
#  xlim(-10000,10000) +
  theme_bw()

#a = 4500
#c = 7068

#print("Absolute Return in 10 years")

#ggplot(t[a:c,],aes(x = port1_absreturn)) + 
#  geom_histogram(binwidth = 1,aes(y=..density..,fill=..count..)) +
#  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port1_absreturn),sd = sd(t$port1_absreturn))) +
#  theme_bw()

#ggplot(t[a:c,],aes(x = port2_absreturn)) + 
#  geom_histogram(binwidth = 1,aes(y=..density..,fill=..count..)) +
#  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port2_absreturn),sd = sd(t$port2_absreturn))) +
#  theme_bw()

#ggplot(t[a:c,],aes(x = port3_absreturn)) + 
#  geom_histogram(binwidth = 1,aes(y=..density..,fill=..count..)) +
#  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port3_absreturn),sd = sd(t$port3_absreturn))) +
#  theme_bw()

#ggplot(t[a:c,],aes(x = port4_absreturn)) + 
#  geom_histogram(binwidth = 1,aes(y=..density..,fill=..count..)) +
#  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port4_absreturn),sd = sd(t$port4_absreturn))) +
#  theme_bw()

```

#Histogram of Percentage Return

```{r Histogram Plot Percentage Return}

ggplot(t,aes(x = port1_Perreturn)) +
  geom_histogram(binwidth = 0.001,aes(y=..density..,fill=..count..)) +
  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port1_Perreturn),sd = sd(t$port1_Perreturn))) +
  theme_bw()

ggplot(t,aes(x = port2_Perreturn)) +
  geom_histogram(binwidth = 0.001,aes(y=..density..,fill=..count..)) +
  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port2_Perreturn),sd = sd(t$port2_Perreturn))) +
  theme_bw()

ggplot(t,aes(x = port3_Perreturn)) +
  geom_histogram(binwidth = 0.001,aes(y=..density..,fill=..count..)) +
  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port3_Perreturn),sd = sd(t$port3_Perreturn))) +
  theme_bw()

ggplot(t,aes(x = port4_Perreturn)) +
  geom_histogram(binwidth = 0.001,aes(y=..density..,fill=..count..)) +
  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port4_Perreturn),sd = sd(t$port4_Perreturn))) +
  theme_bw()

#a = 4500
#c = 7068

#print("Percentage Return in 10 years")

#ggplot(t[a:c,],aes(x = port1_Perreturn)) +
#  geom_histogram(binwidth = 0.001,aes(y=..density..,fill=..count..)) +
#  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port1_Perreturn),sd = sd(t$port1_Perreturn))) +
#  theme_bw()

#ggplot(t[a:c,],aes(x = port2_Perreturn)) +
#  geom_histogram(binwidth = 0.001,aes(y=..density..,fill=..count..)) +
#  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port2_Perreturn),sd = sd(t$port2_Perreturn))) +
#  theme_bw()

#ggplot(t[a:c,],aes(x = port3_Perreturn)) +
#  geom_histogram(binwidth = 0.001,aes(y=..density..,fill=..count..)) +
#  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port3_Perreturn),sd = sd(t$port3_Perreturn))) +
#  theme_bw()

#ggplot(t[a:c,],aes(x = port4_Perreturn)) +
#  geom_histogram(binwidth = 0.001,aes(y=..density..,fill=..count..)) +
#  stat_function(fun = dnorm, color="red", args = list(mean = mean(t$port4_Perreturn),sd = sd(t$port4_Perreturn))) +
#  theme_bw()

```


#QQ plot of Relreturn

```{r QQ Plot Relreturn}

ggplot(t, aes(sample=port1_Relreturn)) +  stat_qq() 
ggplot(t, aes(sample=port2_Relreturn)) +  stat_qq() 
ggplot(t, aes(sample=port3_Relreturn)) +  stat_qq() 
ggplot(t, aes(sample=port4_Relreturn)) +  stat_qq() 

#a = 4500
#c = 7068

#print("Absolute Return in 10 years")

#ggplot(t[a:c,], aes(sample=port1_absreturn)) +  stat_qq() 
#ggplot(t[a:c,], aes(sample=port2_absreturn)) +  stat_qq() 
#ggplot(t[a:c,], aes(sample=port3_absreturn)) +  stat_qq() 
#ggplot(t[a:c,], aes(sample=port4_absreturn)) +  stat_qq() 


```

#QQ plot of Percentage Return

```{r QQ Plot Percentage Return}

ggplot(t, aes(sample=port1_Perreturn)) +  stat_qq()
ggplot(t, aes(sample=port2_Perreturn)) +  stat_qq()
ggplot(t, aes(sample=port3_Perreturn)) +  stat_qq()
ggplot(t, aes(sample=port4_Perreturn)) +  stat_qq()

#a = 4500
#c = 7068

#print("Percentage Return in 10 years")

#ggplot(t[a:c,], aes(sample=port1_Perreturn)) +  stat_qq()
#ggplot(t[a:c,], aes(sample=port2_Perreturn)) +  stat_qq()
#ggplot(t[a:c,], aes(sample=port3_Perreturn)) +  stat_qq()
#ggplot(t[a:c,], aes(sample=port4_Perreturn)) +  stat_qq()


```

#Statistics of Relreturn

```{r Statistics of Relreturn}

cat(red("Relreturn Statistics in all time\n"))
cat(blue("Portfolio 1\n"))
stat.desc(t$port1_Relreturn)
describe(t$port1_Relreturn)

cat(blue("Portfolio 2\n"))
stat.desc(t$port2_Relreturn)
describe(t$port2_Relreturn)

cat(blue("Portfolio 3\n"))
stat.desc(t$port3_Relreturn)
describe(t$port3_Relreturn)

cat(blue("Portfolio 4\n"))
stat.desc(t$port4_Relreturn)
describe(t$port4_Relreturn)

# a = 4500
# c = 7068
# 
# cat(red("absreturn Statistics in 10 years\n"))
# cat(blue("Portfolio 1\n"))
# stat.desc(t$port1_absreturn[a:c])
# describe(t$port1_absreturn[a:c])
# 
# cat(blue("Portfolio 2\n"))
# stat.desc(t$port2_absreturn[a:c])
# describe(t$port2_absreturn[a:c])
# 
# cat(blue("Portfolio 3\n"))
# stat.desc(t$port3_absreturn[a:c])
# describe(t$port3_absreturn[a:c])
# 
# cat(blue("Portfolio 4\n"))
# stat.desc(t$port4_absreturn[a:c])
# describe(t$port4_absreturn[a:c])

```



#Statistics of Percentage Return

```{r Statistics of Percentage Return}

cat(red("Percentage Statistics in all time\n"))
cat(blue("Portfolio 1\n"))
stat.desc(t$port1_Perreturn)
describe(t$port1_Perreturn)

cat(blue("Portfolio 2\n"))
stat.desc(t$port2_Perreturn)
describe(t$port2_Perreturn)

cat(blue("Portfolio 3\n"))
stat.desc(t$port3_Perreturn)
describe(t$port3_Perreturn)

cat(blue("Portfolio 4\n"))
stat.desc(t$port4_Perreturn)
describe(t$port4_Perreturn)

a = 4500
c = 7068

cat(red("Percentage Statistics in 10 years\n"))
cat(blue("Portfolio 1\n"))
stat.desc(t$port1_Perreturn[a:c])
describe(t$port1_Perreturn[a:c])

cat(blue("Portfolio 2\n"))
stat.desc(t$port2_Perreturn[a:c])
describe(t$port2_Perreturn[a:c])

cat(blue("Portfolio 3\n"))
stat.desc(t$port3_Perreturn[a:c])
describe(t$port3_Perreturn[a:c])

cat(blue("Portfolio 4\n"))
stat.desc(t$port4_Perreturn[a:c])
describe(t$port4_Perreturn[a:c])

```

#Statistics Comparison

```{r Statistics table}

base <- t[,c(10,11,12,13)]
colnames(base) <- c("port1_Relreturn","port2_Relreturn","port3_Relreturn","port4_Relreturn")

#base <- t[,c(9,11,13,15)]
#colnames(base) <- c("port1_absreturn","port2_absreturn","port3_absreturn","port4_absreturn")

stat <- sapply(base,sum) %>%
  rbind(sapply(base,mean)) %>%
  rbind(sapply(base,mean)*252) %>%
  rbind(sapply(base,var)) %>%
  rbind(sapply(base,skew)) %>%
  rbind(sapply(base,kurtosis))

rownames(stat) <- c("sum","mean","annual mean","var","skew","kurtosis")

print("Statistics in all time")
print(stat)

# a = 4500
# c = 7068
# 
# stat2 <- sapply(base[a:c,],sum) %>%
#   rbind(sapply(base[a:c,],mean)) %>%
#   rbind(sapply(base[a:c,],mean)*252) %>%
#   rbind(sapply(base[a:c,],var)) %>%
#   rbind(sapply(base[a:c,],skew)) %>%
#   rbind(sapply(base[a:c,],kurtosis))
# 
# rownames(stat2) <- c("sum","mean","annual mean","var","skew","kurtosis") 
# 
# print("Statistics in 10 years")
# print(stat2)


```

#Cumulative RelReturn
See how the cost of options and straddles ruined your return


```{r Cumulative Relreturn}

t$port1_cum_Relreturn <- cumsum(t$port1_Relreturn)
t$port2_cum_Relreturn <- cumsum(t$port2_Relreturn)
t$port3_cum_Relreturn <- cumsum(t$port3_Relreturn)
t$port4_cum_Relreturn <- cumsum(t$port4_Relreturn)

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_cum_Relreturn,color="Port1")) +
  geom_line(aes(y=port2_cum_Relreturn,color="Port2")) +
  geom_line(aes(y=port3_cum_Relreturn,color="Port3")) +
  geom_line(aes(y=port4_cum_Relreturn,color="Port4")) +
#  ylim(-10000000,50000000) +
  theme_bw() +
  ggtitle("Cumulative Return comparing in all time")

# a = 4500
# c = 7068
# t$port1_cum_abs_return2[a:c]<-cumsum(t$port1_Relreturn[a:c])
# t$port2_cum_abs_return2[a:c]<-cumsum(t$port2_Relreturn[a:c])
# t$port3_cum_abs_return2[a:c]<-cumsum(t$port3_Relreturn[a:c])
# t$port4_cum_abs_return2[a:c]<-cumsum(t$port4_Relreturn[a:c])
# 
# ggplot(t[a:c,],aes(x=Date)) + 
#   geom_line(aes(y=port1_cum_abs_return2,color="Port1")) +
#   geom_line(aes(y=port2_cum_abs_return2,color="Port2")) +
#   geom_line(aes(y=port3_cum_abs_return2,color="Port3")) +
#   geom_line(aes(y=port4_cum_abs_return2,color="Port4")) +
#   theme_bw() +
#   ggtitle("abs Return comparing in 10 years")

```
#Culmulative percentage Return(see initiate invest as $1)
See how the cost of options and straddles ruined your return


```{r Culmulative per returns}

t$port1_cum_per_return<-cumsum(t$port1_Perreturn)
t$port2_cum_per_return<-cumsum(t$port2_Perreturn)
t$port3_cum_per_return<-cumsum(t$port3_Perreturn)
t$port4_cum_per_return<-cumsum(t$port4_Perreturn)

ggplot(t,aes(x=Date)) +
  geom_line(aes(y=port1_cum_per_return,color="Port1")) +
  geom_line(aes(y=port2_cum_per_return,color="Port2")) +
  geom_line(aes(y=port3_cum_per_return,color="Port3")) +
  geom_line(aes(y=port4_cum_per_return,color="Port4")) +
  theme_bw() +
  ggtitle("per Return comparing in all time")

a = 4500
c = 7068
t$port1_cum_per_return2[a:c]<-cumsum(t$port1_Perreturn[a:c])
t$port2_cum_per_return2[a:c]<-cumsum(t$port2_Perreturn[a:c])
t$port3_cum_per_return2[a:c]<-cumsum(t$port3_Perreturn[a:c])
t$port4_cum_per_return2[a:c]<-cumsum(t$port4_Perreturn[a:c])

ggplot(t[a:c,],aes(x=Date)) +
  geom_line(aes(y=port1_cum_per_return2,color="Port1")) +
  geom_line(aes(y=port2_cum_per_return2,color="Port2")) +
  geom_line(aes(y=port3_cum_per_return2,color="Port3")) +
  geom_line(aes(y=port4_cum_per_return2,color="Port4")) +
  theme_bw() +
  ggtitle("per Return comparing in 10 years")

```



#Realized Volatility on Relreturn
Realized Vol is limited, 10 years has upper boundary


```{r Realized Volatility}

t$port1_real_vol <- 252*cumsum(t$port1_Relreturn^2)/seq(length(t$port1_Relreturn)) %>% sqrt()
t$port2_real_vol <- 252*cumsum(t$port2_Relreturn^2)/seq(length(t$port2_Relreturn)) %>% sqrt()
t$port3_real_vol <- 252*cumsum(t$port3_Relreturn^2)/seq(length(t$port3_Relreturn)) %>% sqrt()
t$port4_real_vol <- 252*cumsum(t$port4_Relreturn^2)/seq(length(t$port4_Relreturn)) %>% sqrt()

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_real_vol,color="Port1")) +
  geom_line(aes(y=port2_real_vol,color="Port2")) +
  geom_line(aes(y=port3_real_vol,color="Port3")) +
  geom_line(aes(y=port4_real_vol,color="Port4")) +
#  ylim(-1000,10000) +
  theme_bw() +
  ggtitle("Realized Volatility in all time")

# a = 4500
# c = 7068
# 
# t$port1_real_vol2[a:c] <- 252*cumsum(t$port1_absreturn[a:c]^2)/seq(length(t$port1_absreturn[a:c])) %>% sqrt()
# t$port2_real_vol2[a:c] <- 252*cumsum(t$port2_absreturn[a:c]^2)/seq(length(t$port2_absreturn[a:c])) %>% sqrt()
# t$port3_real_vol2[a:c] <- 252*cumsum(t$port3_absreturn[a:c]^2)/seq(length(t$port3_absreturn[a:c])) %>% sqrt()
# t$port4_real_vol2[a:c] <- 252*cumsum(t$port4_absreturn[a:c]^2)/seq(length(t$port4_absreturn[a:c])) %>% sqrt()
# 
# ggplot(t[a:c,],aes(x=Date)) + 
#   geom_line(aes(y=port1_real_vol2,color="Port1")) +
#   geom_line(aes(y=port2_real_vol2,color="Port2")) +
#   geom_line(aes(y=port3_real_vol2,color="Port3")) +
#   geom_line(aes(y=port4_real_vol2,color="Port4")) +
#   theme_bw() +
#   ggtitle("Realized Volatility in 10 years")

```


#Rolling Analysis annually(252 days)
Rolling mean is smoother, bur going worse. 
Rolling vlo is controlled. 
Rolling correlation is towards positive, which is not we expecting.


```{r Rolling Analysis annually}

port1 <- xts(x=t$port1_Relreturn, order.by=t$Date)
port2 <- xts(x=t$port2_Relreturn, order.by=t$Date)
port3 <- xts(x=t$port3_Relreturn, order.by=t$Date)
port4 <- xts(x=t$port4_Relreturn, order.by=t$Date)

t$port1_roll_mean <- apply.rolling(port1,252,gap=252,by=1,FUN="mean")
t$port2_roll_mean <- apply.rolling(port2,252,gap=252,by=1,FUN="mean")
t$port3_roll_mean <- apply.rolling(port3,252,gap=252,by=1,FUN="mean")
t$port4_roll_mean <- apply.rolling(port4,252,gap=252,by=1,FUN="mean")

t$port1_roll_vol <- apply.rolling(port1,252,gap=252,by=1,FUN="sd")
t$port2_roll_vol <- apply.rolling(port2,252,gap=252,by=1,FUN="sd")
t$port3_roll_vol <- apply.rolling(port3,252,gap=252,by=1,FUN="sd")
t$port4_roll_vol <- apply.rolling(port4,252,gap=252,by=1,FUN="sd")


ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_roll_mean,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_roll_mean,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port3_roll_mean,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port4_roll_mean,na.rm = TRUE)) 

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_roll_vol,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_roll_vol,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port3_roll_vol,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port4_roll_vol,na.rm = TRUE))

chart.RollingCorrelation(t$port1_roll_mean, t$port1_roll_vol,252)
chart.RollingCorrelation(t$port2_roll_mean, t$port2_roll_vol,252)
chart.RollingCorrelation(t$port3_roll_mean, t$port3_roll_vol,252)
chart.RollingCorrelation(t$port4_roll_mean, t$port4_roll_vol,252)

```

#Rolling Analysis 60 days
Rolling mean is smoother, bur going worse. 
Rolling vlo is controlled. 
Rolling correlation is towards positive, which is not we expecting.

```{r Rolling Analysis 60 days}

port1 <- xts(x=t$port1_Relreturn, order.by=t$Date)
t$port1_roll_mean <- apply.rolling(port1,60,gap=60,by=1,FUN="mean")
t$port1_roll_vol <- apply.rolling(port1,60,gap=60,by=1,FUN="sd")
port2 <- xts(x=t$port2_Relreturn, order.by=t$Date)
t$port2_roll_mean <- apply.rolling(port2,60,gap=60,by=1,FUN="mean")
t$port2_roll_vol <- apply.rolling(port2,60,gap=60,by=1,FUN="sd")
port3 <- xts(x=t$port3_Relreturn, order.by=t$Date)
t$port3_roll_mean <- apply.rolling(port3,60,gap=60,by=1,FUN="mean")
t$port3_roll_vol <- apply.rolling(port3,60,gap=60,by=1,FUN="sd")
port4 <- xts(x=t$port4_Relreturn, order.by=t$Date)
t$port4_roll_mean <- apply.rolling(port4,60,gap=60,by=1,FUN="mean")
t$port4_roll_vol <- apply.rolling(port4,60,gap=60,by=1,FUN="sd")

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_roll_mean,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_roll_mean,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port3_roll_mean,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port4_roll_mean,na.rm = TRUE)) 


ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_roll_vol,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_roll_vol,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port3_roll_vol,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port4_roll_vol,na.rm = TRUE))


chart.RollingCorrelation(t$port1_roll_mean, t$port1_roll_vol,60)
chart.RollingCorrelation(t$port2_roll_mean, t$port2_roll_vol,60)
chart.RollingCorrelation(t$port3_roll_mean, t$port3_roll_vol,60)
chart.RollingCorrelation(t$port4_roll_mean, t$port4_roll_vol,60)


```






setwd("F:/Dropbox/[IAQF_Max]/R")
write_csv(t,"../data/data.csv")
















