---
title: "Optimal_port2"
author: "Panther"
date: "February 19, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Load Data

```{r Load Data, message=FALSE}
library(quanteda); library(tidyverse); library(TTR);library(ggplot2);library(scales); library(fOptions); library(pastecs); library(psych);library(crayon);library(PerformanceAnalytics);library(stats);library(RQuantLib);

# here data read is being processed
setwd("F:/Dropbox/[IAQF_Max]/R")

#t <- read_csv("../data/data_div.csv")
#t <- read_csv("../Data/data.csv")
#t <- read_csv("F:/Dropbox/[IAQF]/Data/data.csv")
# t$Date <- strptime(as.character(t$Date), "%m/%d/%Y")
# format(t$Date, "%Y-%m-%d")
# t$Date <- as.Date(t$Date)

```

#Process Data

```{r Process Data}

GSPC <- read_csv("../data/^GSPC.csv")
Treasury <- read_csv("../data/DTB3.csv")
VIX <- read_csv("../data/^VIX.csv")
DIV <- read_csv("../data/Dividends.csv")
DIV_M <- read_csv("../data/SP500_DIV_YIELD_MONTH.csv")

# DIV$`SPX Index` <- strptime(as.character(DIV$`SPX Index`), "%m/%d/%Y")
# format(DIV$`SPX Index`, "%Y-%m-%d")
# DIV$`SPX Index` <- as.Date(DIV$`SPX Index`)
# t <- t[-10]

t<-cbind(GSPC,Treasury$DTB3[match(GSPC$Date,Treasury$DATE)])
t<-cbind(t,VIX$Close[match(t$Date,VIX$Date)])
t<-cbind(t,DIV$X2[match(t$Date,DIV$`SPX Index`)])

t<-t[,c(1,5,8,9,10)]
t<- t[-1:(-10054+250),]  # extra 120 for training signal, will remove later
colnames(t)[3] <- "Free_rate"
colnames(t)[4] <- "VIX"
colnames(t)[5] <- "Div_rate_daily"
t$Free_rate = as.numeric(as.character(t$Free_rate))
t$Div_rate_daily = as.numeric(as.character(t$Div_rate_daily))

```

#Missing Data

```{r Missing Data}

#missing data of free rate
temp <- which(is.na(t$Free_rate))
for (i in temp)
  t$Free_rate[i] <- mean(t$Free_rate[(i-5):(i+5)], na.rm=TRUE)

temp <- which(is.na(t$Div_rate_daily))
for (i in temp){
  if (i<15)
    t$Div_rate_daily[i] <- mean(t$Div_rate_daily[1:30], na.rm=TRUE)
  else
    t$Div_rate_daily[i] <- mean(t$Div_rate_daily[(i-15):(i+15)], na.rm=TRUE)}

```

#Smooth dividend daily rate as monthly rate

```{r smooth dividend}

t$Div_rate_monthly <- t$Div_rate_daily
# t$POSIXct_Date <- as.POSIXct(t$Date)
# DIV_M$POSIXct_Date <- as.POSIXct(DIV_M$Date)
DIV_M <- DIV_M[ nrow(DIV_M):1, ]
DIV_M<- DIV_M[-1:-1416,]
temp <- c("2018-01-31",1.87)
DIV_M <- rbind(DIV_M, temp)
DIV_M$Value = as.numeric(DIV_M$Value)
# 

for (i in seq_along(t$Div_rate_daily)){
  for (j in seq_along(DIV_M$Value)){
    if (t$Date[i] <= DIV_M$Date[j+1] && t$Date[i] > DIV_M$Date[j]){
      t$Div_rate_monthly[i] = DIV_M$Value[j+1]/100
      break
    }
  }
}

```

#Moving Average and momentum signal

```{r momentum signal}

t$SMA210 <- SMA(t$Close,210)
t$SMA220 <- SMA(t$Close,220)
t<- t[-1:-250,]      # here remove training 120
for (k in seq_along(t$SMA220)){
  if (t$SMA210[k]>t$SMA220[k])
     t$signal[k] = 1            # signal = 1 is buy singal
  else if (t$SMA210[k]<t$SMA220[k])
     t$signal[k] = 0
  else
     t$signal[k] = t$singal[k-1]
}


```

## Create portfolios
Absolute Return = shift between one lag of close prices
Percentage Return = Absolute Return / last day close price
Relative Return = Percentage return * initiate price($100,000)
We use Relative Return as analysis object

#portfolio 1
Buy/short 1 index on today's closing and close position next day
Assume when you short today, you buy an index for paying back next day
Recieve dividend while buying

```{r portfolio 1}

t$port1_absreturn[1] = NA
#t$port1_Perreturn[1] = NA
t$port1_Relreturn[1] = NA


for (i in seq_along(t$Close[1:(length(t$Close)-1)])){
  if (t$signal[i]== 1){
     t$port1_absreturn[i+1] = (t$Close[i+1]-t$Close[i]+t$Close[i]*t$Div_rate_monthly[i]/365*as.numeric(difftime(t$Date[i+1],t$Date[i])))
#     t$port1_Perreturn[i+1] = (t$Close[i+1]-t$Close[i]) / t$Close[i]
     t$port1_Relreturn[i+1] = (t$Close[i+1]-t$Close[i]+t$Close[i]*t$Div_rate_monthly[i]/365*as.numeric(difftime(t$Date[i+1],t$Date[i]))) / t$Close[i] * 100000
     }
  else{
     t$port1_absreturn[i+1] = t$Close[i]-t$Close[i+1]
#     t$port1_Perreturn[i+1] = (t$Close[i]-t$Close[i+1]) / t$Close[i]
     t$port1_Relreturn[i+1] = (t$Close[i]-t$Close[i+1]) / t$Close[i] * 100000
     }
}

t$port1_Perreturn <- t$port1_Relreturn/100000
```

#portfolio 2
Buy at the money call/put option(90 days maturity) on today's closing and close position next day
Volatility is VIX
Risk free rate is 90 days T-bill rate
Consider dividends

```{r portfolio 2}

t$port2_absreturn[1] = NA
#t$port2_Perreturn[1] = NA
t$port2_Relreturn[1] = NA

for (i in seq_along(t$Close[1:(length(t$Close)-1)])){

  if (t$signal[i]== 1){
    aa <- EuropeanOption("call", t$Close[i+1], t$Close[i],t$Div_rate_monthly[i+1], (t$Free_rate[i+1]/100), (365-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365, (t$VIX[i+1]/100))
    bb <- EuropeanOption("call", t$Close[i], t$Close[i],t$Div_rate_monthly[i], (t$Free_rate[i]/100), 1, (t$VIX[i]/100))
    } else {
    aa <- EuropeanOption("put", t$Close[i+1], t$Close[i],t$Div_rate_monthly[i+1], (t$Free_rate[i+1]/100), (365-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365, (t$VIX[i+1]/100))
    bb <- EuropeanOption("put", t$Close[i], t$Close[i],t$Div_rate_monthly[i], (t$Free_rate[i]/100), 1, (t$VIX[i]/100))
  }
     t$port2_absreturn[i+1] = aa$value-bb$value
#     t$port2_Perreturn[i+1] = (aa$value-bb$value) / bb$value
     t$port2_Relreturn[i+1] = (aa$value-bb$value) / bb$value * 100000
}

t$port2_Perreturn <- t$port2_Relreturn/100000

```


#portfolio 3
Buy at the money straddle(90 days maturity) on today's closing and close position next day
Volatility is VIX
Risk free rate is 90 days T-bill rate
Consider dividends


```{r portfolio 3}

t$port3_absreturn[1] = NA
#t$port3_Perreturn[1] = NA
t$port3_Relreturn[1] = NA

#ca <- GBSOption("c",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))
#cb <- GBSOption("p",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))
#cc = ca@price + cb@price

for (i in seq_along(t$Close[1:(length(t$Close)-1)])){
    aa1 <- EuropeanOption("call", t$Close[i+1], t$Close[i],t$Div_rate_monthly[i+1], (t$Free_rate[i+1]/100), (365-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365, (t$VIX[i+1]/100))
    aa2 <- EuropeanOption("put", t$Close[i+1], t$Close[i],t$Div_rate_monthly[i+1], (t$Free_rate[i+1]/100), (365-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365, (t$VIX[i+1]/100))
    bb1 <- EuropeanOption("call", t$Close[i], t$Close[i],t$Div_rate_monthly[i], (t$Free_rate[i]/100), 1, (t$VIX[i]/100))
    bb2 <- EuropeanOption("put", t$Close[i], t$Close[i],t$Div_rate_monthly[i], (t$Free_rate[i]/100), 1, (t$VIX[i]/100))

    t$port3_absreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value)
#    t$port3_Perreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value) / (bb1$value+bb2$value)
    t$port3_Relreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value) / (bb1$value+bb2$value)*100000
}

t$port3_Perreturn <- t$port3_Relreturn/100000
```


#Dump first day NA return
```{r}
t <- t[-1,]
```


#Momentum effect of portfolio returns
Obvious autocorrelation, large ARMA parameters

```{r Momentum effect}

acf(t$port1_Relreturn,lag.max = 20,type='correlation')
pacf(t$port1_Relreturn,lag.max = 50)

acf(t$port2_Relreturn,lag.max = 20,type='correlation')
pacf(t$port2_Relreturn,lag.max = 50)

acf(t$port3_Relreturn,lag.max = 20,type='correlation')
pacf(t$port3_Relreturn,lag.max = 50)

```

# Scatter of RelReturn

```{r Scatter Plot RelReturn}

ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port1_Relreturn),size =1, shape= 1)

ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port2_Relreturn),size =1, shape= 1)


ggplot(t,aes(x=Date)) + 
  geom_point(aes(y=port3_Relreturn),size =1, shape= 1)

```


#Statistics Comparison

```{r Statistics table}

base <- tt[,c(11,13,15)]
#base <- t[,c(11,14,17)]
colnames(base) <- c("port1_Relreturn","port2_Relreturn","port3_Relreturn")
a1 <- as.xts(base[,1],t$Date)
a2 <- as.xts(base[,2],t$Date)
a3 <- as.xts(base[,3],t$Date)
b <- as.xts(t[,3]/100,t$Date)
c1 = SharpeRatio(a1,b,FUN = "StdDev")
c2 = SharpeRatio(a2,b,FUN = "StdDev")
c3 = SharpeRatio(a3,b,FUN = "StdDev")

stat <- sapply(base,sum) %>%
  rbind(sapply(base,mean)) %>%
  rbind(sapply(base,mean)*252) %>%
  rbind(sapply(base,var)) %>%
  rbind(sapply(base,skew)) %>%
  rbind(sapply(base,kurtosis)) %>%
  rbind(c(c1,c2,c3))

rownames(stat) <- c("sum","mean","annual mean","var","skew","kurtosis","sharp ratio")

print(stat)

```

#Cumulative RelReturn
See how the cost of options and straddles ruined your return


```{r Cumulative Relreturn}

t <- read_csv("../data/data_optimal.csv")
tt <- read_csv("../data/data_final.csv")
t <- t[-1,]
tt <- tt[-1,]

#t$port1_cum_Relreturn <- cumsum(t$port1_Relreturn)
t$port2_cum_Relreturn <- cumsum(t$port2_Relreturn)
#t$port3_cum_Relreturn <- cumsum(t$port3_Relreturn)
t$initial <- cumsum(tt$port2_Relreturn)

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_cum_Relreturn,color="Optimal")) +
  geom_line(aes(y=initial,color="Initial")) +
  theme_bw() +
  ggtitle("Cumulative Return comparison")


```


#Realized Volatility on Relreturn
Realized Vol is limited, 10 years has upper boundary


```{r Realized Volatility}

t$port1_real_vol <- 252*cumsum(t$port1_Relreturn^2)/seq(length(t$port1_Relreturn)) %>% sqrt()
t$port2_real_vol <- 252*cumsum(t$port2_Relreturn^2)/seq(length(t$port2_Relreturn)) %>% sqrt()
t$port3_real_vol <- 252*cumsum(t$port3_Relreturn^2)/seq(length(t$port3_Relreturn)) %>% sqrt()

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_real_vol,color="Port1")) +
  geom_line(aes(y=port2_real_vol,color="Port2")) +
  geom_line(aes(y=port3_real_vol,color="Port3")) +
  theme_bw() +
  ggtitle("Realized Volatility in all time")

```


#Rolling Analysis annually(252 days)
Rolling mean is smoother, bur going worse. 
Rolling vlo is controlled. 
Rolling correlation is towards positive, which is not we expecting.


```{r Rolling Analysis annually}

port1 <- xts(x=t$port1_Relreturn, order.by=t$Date)
port2 <- xts(x=t$port2_Relreturn, order.by=t$Date)
port3 <- xts(x=t$port3_Relreturn, order.by=t$Date)

t$port1_roll_mean <- apply.rolling(port1,252,gap=252,by=1,FUN="mean")
t$port2_roll_mean <- apply.rolling(port2,252,gap=252,by=1,FUN="mean")
t$port3_roll_mean <- apply.rolling(port3,252,gap=252,by=1,FUN="mean")

t$port1_roll_vol <- apply.rolling(port1,252,gap=252,by=1,FUN="sd")
t$port2_roll_vol <- apply.rolling(port2,252,gap=252,by=1,FUN="sd")
t$port3_roll_vol <- apply.rolling(port3,252,gap=252,by=1,FUN="sd")

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_roll_mean,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_roll_mean,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port3_roll_mean,na.rm = TRUE))

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_roll_vol,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_roll_vol,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port3_roll_vol,na.rm = TRUE))

chart.RollingCorrelation(t$port1_roll_mean, t$port1_roll_vol,252)
chart.RollingCorrelation(t$port2_roll_mean, t$port2_roll_vol,252)
chart.RollingCorrelation(t$port3_roll_mean, t$port3_roll_vol,252)

```

#Rolling Analysis 60 days
Rolling mean is smoother, bur going worse. 
Rolling vlo is controlled. 
Rolling correlation is towards positive, which is not we expecting.

```{r Rolling Analysis 60 days}

port1 <- xts(x=t$port1_Relreturn, order.by=t$Date)
t$port1_roll_mean <- apply.rolling(port1,60,gap=60,by=1,FUN="mean")
t$port1_roll_vol <- apply.rolling(port1,60,gap=60,by=1,FUN="sd")
port2 <- xts(x=t$port2_Relreturn, order.by=t$Date)
t$port2_roll_mean <- apply.rolling(port2,60,gap=60,by=1,FUN="mean")
t$port2_roll_vol <- apply.rolling(port2,60,gap=60,by=1,FUN="sd")
port3 <- xts(x=t$port3_Relreturn, order.by=t$Date)
t$port3_roll_mean <- apply.rolling(port3,60,gap=60,by=1,FUN="mean")
t$port3_roll_vol <- apply.rolling(port3,60,gap=60,by=1,FUN="sd")

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_roll_mean,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_roll_mean,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port3_roll_mean,na.rm = TRUE))

ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port1_roll_vol,na.rm = TRUE)) 
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port2_roll_vol,na.rm = TRUE))
ggplot(t,aes(x=Date)) + 
  geom_line(aes(y=port3_roll_vol,na.rm = TRUE))

chart.RollingCorrelation(t$port1_roll_mean, t$port1_roll_vol,60)
chart.RollingCorrelation(t$port2_roll_mean, t$port2_roll_vol,60)
chart.RollingCorrelation(t$port3_roll_mean, t$port3_roll_vol,60)

```




setwd("F:/Dropbox/[IAQF_Max]/R")
write_csv(t,"../Data/data_optimal.csv")
