---
title: "Port1&2"
author: "Panther"
date: "February 16, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Load Data

```{r Load Data, message=FALSE}
library(quanteda); library(tidyverse); library(TTR);library(ggplot2);library(scales); library(fOptions); library(pastecs); library(psych);library(crayon);library(PerformanceAnalytics);library(stats);library(RQuantLib);library(ggrepel);

# here data read is being processed
t <- read_csv("F:/Dropbox/[IAQF]/Data/data_final.csv")
t <- t[-1,]  #dump first day NA

```

##Signal
#Singal turning point
```{r }
#turning point
t$signal_turning[1] = NA
for (i in seq_along(t$Close[1:(length(t$Close)-1)])){
  if (t$signal[i+1] == t$signal[i])  #different from previous day
    t$signal_turning[i+1] = 0
  else
    t$signal_turning[i+1] = 1   #change to and maintain
}

table(t$signal_turning)

temp = which(t$signal_turning == 1)
j = 1
a <- data.frame(date=as.POSIXct(character()),close=as.numeric(),signal=as.numeric())
for (i in temp){
  a[j,1] <- t$Date[i]
  a[j,2] <- t$Close[i]
  a[j,3] <- t$signal[i]
  j = j+1
}

ggplot(t,aes(x=POSIXct_Date)) + 
  geom_line(aes(y=Close,color="Close")) +
  geom_line(aes(y=SMA60,color="SMA60")) +
  geom_line(aes(y=SMA120,color="SMA120"))+ 
  scale_x_datetime(breaks=date_breaks("1 year"),labels = date_format("%y")) +
  labs(color="Legend")+
  scale_colour_manual("", breaks = c("Close", "SMA60","SMA120"),
                          values = c("blue", "red","green")) +
#  geom_point(data=a,aes(x=date,y=close),size =3, shape= 5) +
#  geom_text(data=a, aes(x=date,y=close,label = signal),size = 5,check_overlap = TRUE, vjust = 0.5) +
#  geom_text_repel(data=a, aes(x=date,y=close,label = signal)) +
  geom_label_repel(data=a, aes(x=date,y=close,label = signal),alpha = 0.3)  +
  geom_vline(data=a, aes(xintercept =date),linetype="dotted", size=0.2) +
  theme_bw() +
  ggtitle("Closing index and moving averge for all data")

```

#Profitability of each turning signal
```{r }
#t <- t[-1,] 

mean_return = mean(t$port1_Relreturn)

b <- data.frame(sum_return=as.numeric(),excess_return=as.numeric(),return_ratio=as.numeric(),date=as.Date(character()))
count = 1
for (i in temp){
  if (count == 1){
    b[count,1] <- sum(t$port1_Relreturn[1:i])
    b[count,2] <- b[count,1] - mean_return * i
    b[count,3] <- b[count,1] / (mean_return * i)
    b[count,4] <- t$Date[1]
    temp1 = i
    count = count +1}
  else {
    b[count,1] <- sum(t$port1_Relreturn[temp1:i])
    b[count,2] <- b[count,1] - mean_return * (i-temp1)
    b[count,3] <- b[count,1] / (mean_return * (i-temp1))
    b[count,4] <- t$Date[temp1]
    temp1 = i
    count = count +1}
}
b[count,1] <- sum(t$port1_Relreturn[temp1:length(t$port1_Relreturn)])
b[count,2] <- b[count,1] - mean_return * (length(t$port1_Relreturn)-temp1)
b[count,3] <- b[count,1] / (mean_return * (length(t$port1_Relreturn)-temp1))
b[count,4] <- t$Date[temp1]

which(b$sum_return >0)

b$row <- as.numeric(row.names(b))

ggplot(b,aes(row,sum_return)) +
  geom_bar(stat = "identity",width=1) +
  geom_label_repel(data=b, aes(x=row,label=as.character(date)),size = 3,alpha = 0.5) +
  ggtitle("sum return")

ggplot(b,aes(row,excess_return)) +
  geom_bar(stat = "identity",width=1) +
  geom_label_repel(data=b, aes(x=row,label=as.character(date)),size = 3,alpha = 0.5) +
  ggtitle("excess return")

ggplot(b,aes(row,return_ratio)) +
  geom_bar(stat = "identity",width=1) +
  geom_label_repel(data=b, aes(x=row,label=as.character(date)),size = 3,alpha = 0.5) +
  ggtitle("return ratio")

aa = 0
bb = 0
for (i in b$row) {
  if (i==length(b$row)){
    if (b$sum_return[i]>0)
      aa = aa + as.numeric(difftime(t$Date[length(t$Date)],b$date[i]))
    else
      bb = bb + as.numeric(difftime(t$Date[length(t$Date)],b$date[i]))}
  else {  
    if (b$sum_return[i]>0)
      aa = aa + as.numeric(difftime(b$date[i+1],b$date[i]))
    else
      bb = bb + as.numeric(difftime(b$date[i+1],b$date[i]))} 
}
aa
bb

aaa = 0
bbb = 0
for (i in b$row) {
  if (i==length(b$row)){
    if (b$excess_return[i]>0)
      aaa = aaa + as.numeric(difftime(t$Date[length(t$Date)],b$date[i]))
    else
      bbb = bbb + as.numeric(difftime(t$Date[length(t$Date)],b$date[i]))}
  else {  
    if (b$excess_return[i]>0)
      aaa = aaa + as.numeric(difftime(b$date[i+1],b$date[i]))
    else
      bbb = bbb + as.numeric(difftime(b$date[i+1],b$date[i]))} 
}
aaa
bbb

```

#Quantify signals' profitability on 60 days rolling window
```{r }
port1 <- xts(x=t$port1_Relreturn, order.by=t$Date)
t$port1_roll_mean <- apply.rolling(port1,60,gap=60,by=1,FUN="mean")
rolling_mean = mean(t$port1_roll_mean,na.rm=TRUE)

c <- data.frame(return_60days=as.numeric(),excess_return=as.numeric(),return_ratio=as.numeric(),date=as.Date(character()))
for (i in seq_along(t$Close[1:(length(t$Close)-60)])){
  c[i,1] <- sum(t$port1_Relreturn[i:i+59])
  c[i,2] <- c[i,1] - rolling_mean*60
  c[i,3] <- c[i,1] / (rolling_mean*60)
  c[i,4] <- t$Date[i]
}

ggplot(c,aes(x=date)) + 
  geom_point(aes(y=return_60days),size =1, shape= 1)

ggplot(c,aes(x=date)) + 
  geom_point(aes(y=excess_return),size =1, shape= 1)

ggplot(c,aes(x=date)) + 
  geom_point(aes(y=return_ratio),size =1, shape= 1)

cc = 0
dd = 0
cc_sum = 0
dd_sum = 0
for (i in seq_along(c$return_60days)) {
  if (c$return_60days[i]>0){
    cc = cc + 1
    cc_sum = cc_sum + c$return_60days[i]}
  else {
    dd = dd + 1
    dd_sum = dd_sum + c$return_60days[i]}
}
cc
dd
cc_sum
dd_sum
cc/cc_sum
dd/dd_sum

```

#Quantify signals' profitability on 252 days rolling window
```{r }
port1 <- xts(x=t$port1_Relreturn, order.by=t$Date)
t$port1_roll_mean <- apply.rolling(port1,252,gap=252,by=1,FUN="mean")
rolling_mean = mean(t$port1_roll_mean,na.rm=TRUE)

c <- data.frame(return_60days=as.numeric(),excess_return=as.numeric(),return_ratio=as.numeric(),date=as.Date(character()))
for (i in seq_along(t$Close[1:(length(t$Close)-252)])){
  c[i,1] <- sum(t$port1_Relreturn[i:i+251])
  c[i,2] <- c[i,1] - rolling_mean*252
  c[i,3] <- c[i,1] / (rolling_mean*252)
  c[i,4] <- t$Date[i]
}

ggplot(c,aes(x=date)) + 
  geom_point(aes(y=return_60days),size =1, shape= 1)

ggplot(c,aes(x=date)) + 
  geom_point(aes(y=excess_return),size =1, shape= 1)

ggplot(c,aes(x=date)) + 
  geom_point(aes(y=return_ratio),size =1, shape= 1)

cc = 0
dd = 0
cc_sum = 0
dd_sum = 0
for (i in seq_along(c$return_60days)) {
  if (c$return_60days[i]>0){
    cc = cc + 1
    cc_sum = cc_sum + c$return_60days[i]}
  else {
    dd = dd + 1
    dd_sum = dd_sum + c$return_60days[i]}
}
cc
dd
cc_sum
dd_sum
cc/cc_sum
dd/dd_sum

```
#Profitability of each turning signal ( portfolio 2)
```{r }
#t <- t[-1,] 

mean_return = mean(t$port2_Relreturn)

b <- data.frame(sum_return=as.numeric(),excess_return=as.numeric(),return_ratio=as.numeric(),date=as.Date(character()))
count = 1
for (i in temp){
  if (count == 1){
    b[count,1] <- sum(t$port2_Relreturn[1:i])
    b[count,2] <- b[count,1] - mean_return * i
    b[count,3] <- b[count,1] / (mean_return * i)
    b[count,4] <- t$Date[1]
    temp1 = i
    count = count +1}
  else {
    b[count,1] <- sum(t$port2_Relreturn[temp1:i])
    b[count,2] <- b[count,1] - mean_return * (i-temp1)
    b[count,3] <- b[count,1] / (mean_return * (i-temp1))
    b[count,4] <- t$Date[temp1]
    temp1 = i
    count = count +1}
}
b[count,1] <- sum(t$port2_Relreturn[temp1:length(t$port2_Relreturn)])
b[count,2] <- b[count,1] - mean_return * (length(t$port2_Relreturn)-temp1)
b[count,3] <- b[count,1] / (mean_return * (length(t$port2_Relreturn)-temp1))
b[count,4] <- t$Date[temp1]

which(b$sum_return >0)

b$row <- as.numeric(row.names(b))

ggplot(b,aes(row,sum_return)) +
  geom_bar(stat = "identity",width=1) +
  geom_label_repel(data=b, aes(x=row,label=as.character(date)),size = 3,alpha = 0.5) +
  ggtitle("sum return")

ggplot(b,aes(row,excess_return)) +
  geom_bar(stat = "identity",width=1) +
  geom_label_repel(data=b, aes(x=row,label=as.character(date)),size = 3,alpha = 0.5) +
  ggtitle("excess return")

ggplot(b,aes(row,return_ratio)) +
  geom_bar(stat = "identity",width=1) +
  geom_label_repel(data=b, aes(x=row,label=as.character(date)),size = 3,alpha = 0.5) +
  ggtitle("return ratio")

aa = 0
bb = 0
for (i in b$row) {
  if (i==length(b$row)){
    if (b$sum_return[i]>0)
      aa = aa + as.numeric(difftime(t$Date[length(t$Date)],b$date[i]))
    else
      bb = bb + as.numeric(difftime(t$Date[length(t$Date)],b$date[i]))}
  else {  
    if (b$sum_return[i]>0)
      aa = aa + as.numeric(difftime(b$date[i+1],b$date[i]))
    else
      bb = bb + as.numeric(difftime(b$date[i+1],b$date[i]))} 
}
aa
bb

aaa = 0
bbb = 0
for (i in b$row) {
  if (i==length(b$row)){
    if (b$excess_return[i]>0)
      aaa = aaa + as.numeric(difftime(t$Date[length(t$Date)],b$date[i]))
    else
      bbb = bbb + as.numeric(difftime(t$Date[length(t$Date)],b$date[i]))}
  else {  
    if (b$excess_return[i]>0)
      aaa = aaa + as.numeric(difftime(b$date[i+1],b$date[i]))
    else
      bbb = bbb + as.numeric(difftime(b$date[i+1],b$date[i]))} 
}
aaa
bbb

```

#Quantify signals' profitability on 60 days rolling window (Portfolio 2)
```{r }
port2 <- xts(x=t$port2_Relreturn, order.by=t$Date)
t$port2_roll_mean <- apply.rolling(port2,60,gap=60,by=1,FUN="mean")
rolling_mean = mean(t$port2_roll_mean,na.rm=TRUE)

c <- data.frame(return_60days=as.numeric(),excess_return=as.numeric(),return_ratio=as.numeric(),date=as.Date(character()))
for (i in seq_along(t$Close[1:(length(t$Close)-60)])){
  c[i,1] <- sum(t$port2_Relreturn[i:i+59])
  c[i,2] <- c[i,1] - rolling_mean*60
  c[i,3] <- c[i,1] / (rolling_mean*60)
  c[i,4] <- t$Date[i]
}

ggplot(c,aes(x=date)) + 
  geom_point(aes(y=return_60days),size =1, shape= 1)

ggplot(c,aes(x=date)) + 
  geom_point(aes(y=excess_return),size =1, shape= 1)

ggplot(c,aes(x=date)) + 
  geom_point(aes(y=return_ratio),size =1, shape= 1)

cc = 0
dd = 0
cc_sum = 0
dd_sum = 0
for (i in seq_along(c$return_60days)) {
  if (c$return_60days[i]>0){
    cc = cc + 1
    cc_sum = cc_sum + c$return_60days[i]}
  else {
    dd = dd + 1
    dd_sum = dd_sum + c$return_60days[i]}
}
cc
dd
cc_sum
dd_sum
cc/cc_sum
dd/dd_sum

```

##Portfolio2 - Option

#Price level
```{r }
ggplot(t,aes(x=POSIXct_Date)) + 
  geom_line(aes(y=Close,color="Close")) +
  scale_x_datetime(breaks=date_breaks("1 year"),labels = date_format("%y")) +
  labs(color="Legend")


S <- xts(x=t$Close, order.by=t$Date)
q <- xts(x=t$Div_rate_monthly, order.by=t$Date)
r <- xts(x=t$Free_rate, order.by=t$Date)
vix <- xts(x=t$VIX, order.by=t$Date)
T = 90

S1 <- apply.rolling(S,252,gap=0,by=252,FUN="mean")
q1 <- apply.rolling(q,252,gap=0,by=252,FUN="mean")
r1 <- apply.rolling(r,252,gap=0,by=252,FUN="mean")
vix1 <- apply.rolling(vix,252,gap=0,by=252,FUN="mean")

S2 <- S1[which(!is.na(S1))]
q2 <- q1[which(!is.na(q1))]
r2 <- r1[which(!is.na(r1))]/100
vix2 <- vix1[which(!is.na(vix1))]/100
T2 <- T/365

#C <- EuropeanOption("call", S2, S2, q2, r2, T2, vix2)
#P <- EuropeanOption("put", S2, S2, q2, r2, T2, vix2)
C <- list()
P <- list()
for (i in seq_along(S2)){
  C[[i]] <- EuropeanOption("call", S2[i], S2[i], q2[i], r2[i], T2, vix2[i])
  P[[i]] <- EuropeanOption("put", S2[i], S2[i], q2[i], r2[i], T2, vix2[i])
}

#date <- data.frame(date=index(S2))

table1 <- data.frame(date=as.Date(character()),index=as.numeric(),callPrice=as.numeric(),callDelta=as.numeric(),putPrice=as.numeric(),putDelta=as.numeric())

for (i in seq_along(S2)){
  table1[i,1] <- as.Date(index(S2[i]))
  table1[i,2] <- S2[[i]]
  table1[i,3] <- C[[i]]$value
  table1[i,4] <- C[[i]]$delta
  table1[i,5] <- P[[i]]$value
  table1[i,6] <- P[[i]]$delta  
}

table1[,7] <- table1[,2]/table1[,3]*table1[,4]
table1[,8] <- table1[,2]/table1[,5]*table1[,6]

colnames(table1)[7] <- "callPortDelta"
colnames(table1)[8] <- "putPortDelta"

print(table1)

t$port2_cum_Relreturn <- cumsum(t$port2_Relreturn)
ggplot(t,aes(x=POSIXct_Date)) + 
  geom_line(aes(y=t$port2_cum_Relreturn,color="Cum_port2_rel")) +
  scale_x_datetime(breaks=date_breaks("1 year"),labels = date_format("%y")) +
  labs(color="Legend")

ggplot(table1,aes(x=date)) + 
#  geom_line(aes(y=index,color="index")) +
  geom_line(aes(y=callPortDelta,color="call port delta")) +
  geom_line(aes(y=putPortDelta,color="put port delta")) +
  labs(color="Legend")



#C[[i]]$  
#   value    delta    gamma     vega    theta      rho   divRho

```

#VIX
```{r }

ggplot(t,aes(x=POSIXct_Date)) + 
  geom_line(aes(y=VIX,color="VIX")) +
  scale_x_datetime(breaks=date_breaks("1 year"),labels = date_format("%y")) +
  labs(color="Legend")

ggplot(table1,aes(x=POSIXct_Date)) + 
  geom_line(aes(y=VIX,color="VIX")) +
  scale_x_datetime(breaks=date_breaks("1 year"),labels = date_format("%y")) +
  labs(color="Legend")

table2 <- data.frame(date=as.Date(character()),VIX=as.numeric(),callPrice=as.numeric(),callVega=as.numeric(),putPrice=as.numeric(),putVega=as.numeric())

for (i in seq_along(S2)){
  table2[i,1] <- as.Date(index(S2[i]))
  table2[i,2] <- vix2[[i]]
  table2[i,3] <- C[[i]]$value
  table2[i,4] <- C[[i]]$vega
  table2[i,5] <- P[[i]]$value
  table2[i,6] <- P[[i]]$vega  
}

ggplot(table2,aes(x=date)) + 
  geom_line(aes(y=callVega,color="Vega")) 

```

#r & Div
```{r }

ggplot(t,aes(x=POSIXct_Date)) + 
  geom_line(aes(y=Free_rate/100,color="r")) +
  geom_line(aes(y=Div_rate_monthly,color="q")) +
  scale_x_datetime(breaks=date_breaks("1 year"),labels = date_format("%y")) +
  labs(color="Legend")


table3 <- data.frame(date=as.Date(character()),r=as.numeric(),callRho=as.numeric(),putRho=as.numeric(),q=as.numeric(),callDivRho=as.numeric(),putDivRho=as.numeric())

for (i in seq_along(S2)){
  table3[i,1] <- as.Date(index(S2[i]))
  table3[i,2] <- r2[[i]]
  table3[i,3] <- C[[i]]$rho
  table3[i,4] <- P[[i]]$rho
  table3[i,5] <- q2[[i]]
  table3[i,6] <- P[[i]]$divRho
  table3[i,7] <- P[[i]]$divRho  
}

ggplot(table3,aes(x=date)) + 
  geom_line(aes(y=callRho,color="Rho")) +
  geom_line(aes(y=callDivRho,color="DivRho"))

```

#T
```{r }

table4 <- data.frame(date=as.Date(character()),callTheta=as.numeric(),putTheta=as.numeric())

for (i in seq_along(S2)){
  table4[i,1] <- as.Date(index(S2[i]))
  table4[i,2] <- C[[i]]$theta
  table4[i,3] <- C[[i]]$theta
}

ggplot(table4,aes(x=date)) + 
  geom_line(aes(y=callTheta,color="callTheta")) +
  geom_line(aes(y=putTheta,color="putTheta"))

T = 180
T2 <- T/365

#C <- EuropeanOption("call", S2, S2, q2, r2, T2, vix2)
#P <- EuropeanOption("put", S2, S2, q2, r2, T2, vix2)
C <- list()
P <- list()
for (i in seq_along(S2)){
  C[[i]] <- EuropeanOption("call", S2[i], S2[i], q2[i], r2[i], T2, vix2[i])
  P[[i]] <- EuropeanOption("put", S2[i], S2[i], q2[i], r2[i], T2, vix2[i])
}

for (i in seq_along(S2)){
  table4[i,1] <- as.Date(index(S2[i]))
  table4[i,2] <- C[[i]]$theta
  table4[i,3] <- C[[i]]$theta
}

ggplot(table4,aes(x=date)) + 
  geom_line(aes(y=callTheta,color="callTheta")) +
  geom_line(aes(y=putTheta,color="putTheta"))


T = 45
T2 <- T/365

#C <- EuropeanOption("call", S2, S2, q2, r2, T2, vix2)
#P <- EuropeanOption("put", S2, S2, q2, r2, T2, vix2)
C <- list()
P <- list()
for (i in seq_along(S2)){
  C[[i]] <- EuropeanOption("call", S2[i], S2[i], q2[i], r2[i], T2, vix2[i])
  P[[i]] <- EuropeanOption("put", S2[i], S2[i], q2[i], r2[i], T2, vix2[i])
}

for (i in seq_along(S2)){
  table4[i,1] <- as.Date(index(S2[i]))
  table4[i,2] <- C[[i]]$theta
  table4[i,3] <- C[[i]]$theta
}

ggplot(table4,aes(x=date)) + 
  geom_line(aes(y=callTheta,color="callTheta")) +
  geom_line(aes(y=putTheta,color="putTheta"))





```

#factor model on all components
```{r }

t$VIX <- t$VIX/100
t$Free_rate <- t$Free_rate/100
t$signal <- factor(t$signal)
tt <- cbind(t$port2_Relreturn,t$Close,t$signal,t$VIX,t$Free_rate,t$Div_rate_monthly)
colnames(tt) <- c("return","close","signal","VIX","Free_rate","Div")
tt <- data.frame(tt)

Mod1 <- lm(return ~ close+signal+VIX+Free_rate+Div, data=tt)
summary(Mod1)

lmMod <- lm(return ~ . , data = tt)
selectedMod <- step(lmMod)
summary(selectedMod)


selectedMod <- lm(return ~ close+signal+VIX+Free_rate+Div, data=tt)
all_vifs <- car::vif(selectedMod)
print(all_vifs)

signif_all <- names(all_vifs)

# Remove vars with VIF> 4 and re-build model until none of VIFs don't exceed 4.
while(any(all_vifs > 4)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))  # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("return ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=inputData)  # re-build model with new formula
  all_vifs <- car::vif(selectedMod)
}
summary(selectedMod)


all_vars <- names(selectedMod[[1]])[-1]  # names of all X variables
# Get the non-significant vars
summ <- summary(selectedMod)  # model summary
pvals <- summ[[4]][, 4]  # get all p values
not_significant <- character()  # init variables that aren't statsitically significant
not_significant <- names(which(pvals > 0.1))
not_significant <- not_significant[!not_significant %in% "(Intercept)"]  # remove 'intercept'. Optional!

# If there are any non-significant variables, 
while(length(not_significant) > 0){
  all_vars <- all_vars[!all_vars %in% not_significant[1]]
  myForm <- as.formula(paste("return ~ ", paste (all_vars, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=tt)  # re-build model with new formula
  
  # Get the non-significant vars.
  summ <- summary(selectedMod)
  pvals <- summ[[4]][, 4]
  not_significant <- character()
  not_significant <- names(which(pvals > 0.1))
  not_significant <- not_significant[!not_significant %in% "(Intercept)"]
}
summary(selectedMod)

library(leaps)

regsubsetsObj <- regsubsets(x=tt[,2:6] ,y=tt$return, nbest = 2, really.big = T)
plot(regsubsetsObj, scale = "adjr2")  # regsubsets plot based on R-sq

Mod2 <- lm(return ~ close, data=tt)
summary(Mod2)


```

#factor model on all components(monthly)
```{r }

ttt=xts(tt[,2:7], order.by=tt$`t$Date`)
tttt=daily2monthly(ttt, FUN=mean, na.rm=TRUE)
#date <- index(tttt)
tttt <- data.frame(tttt)



Mod1 <- lm(return ~ close+signal+VIX+Free_rate+Div, data=tttt)
summary(Mod1)

lmMod <- lm(return ~ . , data = tttt)
selectedMod <- step(lmMod)
summary(selectedMod)


selectedMod <- lm(return ~ close+signal+VIX+Free_rate+Div, data=tt)
all_vifs <- car::vif(selectedMod)
print(all_vifs)

signif_all <- names(all_vifs)

# Remove vars with VIF> 4 and re-build model until none of VIFs don't exceed 4.
while(any(all_vifs > 4)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))  # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("return ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=inputData)  # re-build model with new formula
  all_vifs <- car::vif(selectedMod)
}
summary(selectedMod)


all_vars <- names(selectedMod[[1]])[-1]  # names of all X variables
# Get the non-significant vars
summ <- summary(selectedMod)  # model summary
pvals <- summ[[4]][, 4]  # get all p values
not_significant <- character()  # init variables that aren't statsitically significant
not_significant <- names(which(pvals > 0.1))
not_significant <- not_significant[!not_significant %in% "(Intercept)"]  # remove 'intercept'. Optional!

# If there are any non-significant variables, 
while(length(not_significant) > 0){
  all_vars <- all_vars[!all_vars %in% not_significant[1]]
  myForm <- as.formula(paste("return ~ ", paste (all_vars, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=tt)  # re-build model with new formula
  
  # Get the non-significant vars.
  summ <- summary(selectedMod)
  pvals <- summ[[4]][, 4]
  not_significant <- character()
  not_significant <- names(which(pvals > 0.1))
  not_significant <- not_significant[!not_significant %in% "(Intercept)"]
}
summary(selectedMod)

library(leaps)
regsubsetsObj <- regsubsets(x=tttt[,2:6] ,y=tttt$return, nbest = 2, really.big = T)
plot(regsubsetsObj, scale = "adjr2")  # regsubsets plot based on R-sq

Mod2 <- lm(return ~ close, data=tt)
summary(Mod2)

Mod2 <- lm(return ~ signal, data=tttt)
summary(Mod2)


```










































