---
title: "Portfolio Structuring"
author: "Panther"
date: "February 9, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Load Data

```{r Load Data, message=FALSE}
library(quanteda); library(tidyverse); library(TTR);library(ggplot2);library(scales); library(fOptions); library(pastecs); library(psych);library(crayon);library(PerformanceAnalytics);library(stats);library(RQuantLib);

# here data read is being processed
setwd("F:/Dropbox/[IAQF_Max]/R")

#t <- read_csv("../data/data_div.csv")
#t <- read_csv("../Data/data.csv")
#t <- read_csv("F:/Dropbox/[IAQF]/Data/data.csv")
# t$Date <- strptime(as.character(t$Date), "%m/%d/%Y")
# format(t$Date, "%Y-%m-%d")
# t$Date <- as.Date(t$Date)

```

#Process Data

```{r Process Data}

GSPC <- read_csv("../data/^GSPC.csv")
Treasury <- read_csv("../data/DTB3.csv")
VIX <- read_csv("../data/^VIX.csv")
DIV <- read_csv("../data/Dividends.csv")
DIV_M <- read_csv("../data/SP500_DIV_YIELD_MONTH.csv")

# DIV$`SPX Index` <- strptime(as.character(DIV$`SPX Index`), "%m/%d/%Y")
# format(DIV$`SPX Index`, "%Y-%m-%d")
# DIV$`SPX Index` <- as.Date(DIV$`SPX Index`)
# t <- t[-10]

t<-cbind(GSPC,Treasury$DTB3[match(GSPC$Date,Treasury$DATE)])
t<-cbind(t,VIX$Close[match(t$Date,VIX$Date)])
t<-cbind(t,DIV$X2[match(t$Date,DIV$`SPX Index`)])

t<-t[,c(1,5,8,9,10)]
t<- t[-1:(-10054+120),]  # extra 120 for training signal, will remove later
colnames(t)[3] <- "Free_rate"
colnames(t)[4] <- "VIX"
colnames(t)[5] <- "Div_rate_daily"
t$Free_rate = as.numeric(as.character(t$Free_rate))
t$Div_rate_daily = as.numeric(as.character(t$Div_rate_daily))

```

#Missing Data

```{r Missing Data}

sum(is.na(t))
sum(is.na(t$Close))
sum(is.na(t$Free_rate))
sum(is.na(t$VIX))
sum(is.na(t$Div_rate_daily))
sum(is.na(DIV_M))

which(is.na(t$Free_rate))
#count(which(is.na(t$Free_rate)))
which(is.na(t$VIX)) #don't worry, this missing 120 is not needed
which(is.na(t$Div_rate_daily))

#missing data of free rate
temp <- which(is.na(t$Free_rate))
for (i in temp)
  t$Free_rate[i] <- mean(t$Free_rate[(i-5):(i+5)], na.rm=TRUE)

t$Div_rate_daily[2] <- mean(t$Div_rate_daily[1:32], na.rm=TRUE)
t$Div_rate_daily[7] <- mean(t$Div_rate_daily[1:32], na.rm=TRUE)
temp <- which(is.na(t$Div_rate_daily))
for (i in temp)
  t$Div_rate_daily[i] <- mean(t$Div_rate_daily[(i-15):(i+15)], na.rm=TRUE)

sum(is.na(t$Free_rate))
sum(is.na(t$Div_rate_daily))

```

#Smooth dividend daily rate as monthly rate

```{r smooth dividend}

t$Div_rate_monthly <- t$Div_rate_daily
# t$POSIXct_Date <- as.POSIXct(t$Date)
# DIV_M$POSIXct_Date <- as.POSIXct(DIV_M$Date)
DIV_M <- DIV_M[ nrow(DIV_M):1, ]
DIV_M<- DIV_M[-1:-1416,]
temp <- c("2018-01-31",1.87)
DIV_M <- rbind(DIV_M, temp)
DIV_M$Value = as.numeric(DIV_M$Value)
# 
# for (i in seq_along(t$Div_rate_daily)){
#   if (i < 16)
#     t$Div_rate_monthly[i] = mean(t$Div_rate_daily[i:(i+30)], na.rm=TRUE)
#   else
#     t$Div_rate_monthly[i] = mean(t$Div_rate_daily[(i-15):(i+15)], na.rm=TRUE)}
# 
# ggplot(t,aes(x=Date)) + 
#   geom_line(aes(y=Div_rate_daily))
# ggplot(t,aes(x=Date)) + 
#   geom_line(aes(y=Div_rate_monthly)) 
# 
# stat.desc(t$Div_rate_daily)
# describe(t$Div_rate_daily)
# stat.desc(t$Div_rate_monthly)
# describe(t$Div_rate_monthly)

for (i in seq_along(t$Div_rate_daily)){
  for (j in seq_along(DIV_M$Value)){
    if (t$Date[i] <= DIV_M$Date[j+1] && t$Date[i] > DIV_M$Date[j]){
      t$Div_rate_monthly[i] = DIV_M$Value[j+1]/100
      break
    }
  }
}

```



#Moving Average and momentum signal

```{r momentum signal}

t$SMA60 <- SMA(t$Close,60)
t$SMA120 <- SMA(t$Close,120)
t<- t[-1:-120,]     # here remove training 120
for (i in seq_along(t$SMA120)){
  if (t$SMA60[i]>t$SMA120[i])
     t$signal[i] = 1            # signal = 1 is buy singal
  else if (t$SMA60[i]<t$SMA120[i])
     t$signal[i] = 0
  else
     t$signal[i] = t$singal[i-1]
}

```



## Create portfolios
Absolute Return = shift between one lag of close prices
Percentage Return = Absolute Return / last day close price
Relative Return = Percentage return * initiate price($100,000)
We use Relative Return as analysis object

#portfolio 1
Buy/short 1 index on today's closing and close position next day
Assume when you short today, you buy an index for paying back next day
Recieve dividend while buying

```{r portfolio 1}

t$port1_absreturn[1] = NA
#t$port1_Perreturn[1] = NA
t$port1_Relreturn[1] = NA


for (i in seq_along(t$Close[1:(length(t$Close)-1)])){
  if (t$signal[i]== 1){
     t$port1_absreturn[i+1] = (t$Close[i+1]-t$Close[i]+t$Close[i]*t$Div_rate_monthly[i]/365*as.numeric(difftime(t$Date[i+1],t$Date[i])))
#     t$port1_Perreturn[i+1] = (t$Close[i+1]-t$Close[i]) / t$Close[i]
     t$port1_Relreturn[i+1] = (t$Close[i+1]-t$Close[i]+t$Close[i]*t$Div_rate_monthly[i]/365*as.numeric(difftime(t$Date[i+1],t$Date[i]))) / t$Close[i] * 100000
     }
  else{
     t$port1_absreturn[i+1] = t$Close[i]-t$Close[i+1]
#     t$port1_Perreturn[i+1] = (t$Close[i]-t$Close[i+1]) / t$Close[i]
     t$port1_Relreturn[i+1] = (t$Close[i]-t$Close[i+1]) / t$Close[i] * 100000
     }
}

t$port1_Perreturn <- t$port1_Relreturn/100000
```

#portfolio 2
Buy at the money call/put option(90 days maturity) on today's closing and close position next day
Volatility is VIX
Risk free rate is 90 days T-bill rate
Consider dividends

```{r portfolio 2}

t$port2_absreturn[1] = NA
#t$port2_Perreturn[1] = NA
t$port2_Relreturn[1] = NA

#if (t$signal[1] == 1) {
#  cc <- GBSOption("c",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))
#  } else {
#  cc <- GBSOption("p",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))

# for (i in seq_along(t$Close[1:(length(t$Close)-1)])){
#
#   if (t$signal[i]== 1){
#      aa <- GBSOption("c",t$Close[i+1],t$Close[i],(90-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365,(t$Free_rate[i+1]/100),0,(t$VIX[i+1]/100))
#      bb <- GBSOption("c",t$Close[i],t$Close[i],0.246575342,(t$Free_rate[i]/100),0,(t$VIX[i]/100))
#     } else{
#      aa <- GBSOption("p",t$Close[i+1],t$Close[i],(90-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365,(t$Free_rate[i+1]/100),0,(t$VIX[i+1]/100))
#      bb <- GBSOption("p",t$Close[i],t$Close[i],0.246575342,(t$Free_rate[i]/100),0,(t$VIX[i]/100))
#     }
#      t$port2_absreturn[i+1] = aa@price-bb@price
#      t$port2_Perreturn[i+1] = (aa@price-bb@price) / bb@price
# #     t$port2_Relreturn[i+1] = t$port2_Perreturn[i+1] * t$Close[1]
# }

for (i in seq_along(t$Close[1:(length(t$Close)-1)])){

  if (t$signal[i]== 1){
    aa <- EuropeanOption("call", t$Close[i+1], t$Close[i],t$Div_rate_monthly[i+1], (t$Free_rate[i+1]/100), (90-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365, (t$VIX[i+1]/100))
    bb <- EuropeanOption("call", t$Close[i], t$Close[i],t$Div_rate_monthly[i], (t$Free_rate[i]/100), 0.246575342, (t$VIX[i]/100))
    } else {
    aa <- EuropeanOption("put", t$Close[i+1], t$Close[i],t$Div_rate_monthly[i+1], (t$Free_rate[i+1]/100), (90-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365, (t$VIX[i+1]/100))
    bb <- EuropeanOption("put", t$Close[i], t$Close[i],t$Div_rate_monthly[i], (t$Free_rate[i]/100), 0.246575342, (t$VIX[i]/100))
  }
     t$port2_absreturn[i+1] = aa$value-bb$value
#     t$port2_Perreturn[i+1] = (aa$value-bb$value) / bb$value
     t$port2_Relreturn[i+1] = (aa$value-bb$value) / bb$value * 100000
}

t$port2_Perreturn <- t$port2_Relreturn/100000

```


#portfolio 3
Buy at the money straddle(90 days maturity) on today's closing and close position next day
Volatility is VIX
Risk free rate is 90 days T-bill rate
Consider dividends


```{r portfolio 3}

t$port3_absreturn[1] = NA
#t$port3_Perreturn[1] = NA
t$port3_Relreturn[1] = NA

#ca <- GBSOption("c",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))
#cb <- GBSOption("p",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))
#cc = ca@price + cb@price

for (i in seq_along(t$Close[1:(length(t$Close)-1)])){
    aa1 <- EuropeanOption("call", t$Close[i+1], t$Close[i],t$Div_rate_monthly[i+1], (t$Free_rate[i+1]/100), (90-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365, (t$VIX[i+1]/100))
    aa2 <- EuropeanOption("put", t$Close[i+1], t$Close[i],t$Div_rate_monthly[i+1], (t$Free_rate[i+1]/100), (90-as.numeric(difftime(t$Date[i+1],t$Date[i])))/365, (t$VIX[i+1]/100))
    bb1 <- EuropeanOption("call", t$Close[i], t$Close[i],t$Div_rate_monthly[i], (t$Free_rate[i]/100), 0.246575342, (t$VIX[i]/100))
    bb2 <- EuropeanOption("put", t$Close[i], t$Close[i],t$Div_rate_monthly[i], (t$Free_rate[i]/100), 0.246575342, (t$VIX[i]/100))

    t$port3_absreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value)
#    t$port3_Perreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value) / (bb1$value+bb2$value)
    t$port3_Relreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value) / (bb1$value+bb2$value)*100000
}

t$port3_Perreturn <- t$port3_Relreturn/100000
```

#portfolio 4
Buy at the money straddle(90 days maturity but remain life decrease until rebalance at maturity)
- on today's closing and close position next day
Volatility is VIX
Risk free rate is 90 days T-bill rate
Consider dividends

```{r portfolio 4}

#t$port4_absreturn[1] = NA
#t$port4_Perreturn[1] = NA
t$port4_Relreturn[1] = NA

#ca <- GBSOption("c",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))
#cb <- GBSOption("p",t$Close[1],t$Close[1],0.246575342,(t$Free_rate[1]/100),0,(t$VIX[1]/100))
#cc = ca@price + cb@price

#date.lookup <- format(seq(as.Date("2000-01-02"), as.Date("2018-1-19"), by = "1 day"))
#date.except <- subset(b, !(y %in% a$x))
#match("2024-01-19", date.lookup)

count=0   #count days passed

for (i in seq_along(t$Close[1:(length(t$Close)-1)])){

  if (as.numeric(difftime(t$Date[i+1],t$Date[i])) == 1){   #workday
    count = count+1}
  else {                                            # not workday
    count = count+as.numeric(difftime(t$Date[i+1],t$Date[i])) }

  if (count <= 89){
    Remaina = 90 - count         # today's remain
    Remainb = Remaina + 1}        # previous day's remain
  else if (count >= 90) {       # expired already, adjuste to 90 days passed
    Remaina = 0                 # today's remain
    Remainb = 1                 # previous day's remain
    count = 0 }                 # after expired, rebalance

  aa1 <- EuropeanOption("call", t$Close[i+1], t$Close[i],t$Div_rate_monthly[i+1], (t$Free_rate[i+1]/100), 0.246575342*Remaina/90, (t$VIX[i+1]/100),0, 0)
  aa2 <- EuropeanOption("put", t$Close[i+1], t$Close[i],t$Div_rate_monthly[i+1], (t$Free_rate[i+1]/100), 0.246575342*Remaina/90, (t$VIX[i+1]/100),0, 0)
  bb1 <- EuropeanOption("call", t$Close[i], t$Close[i],t$Div_rate_monthly[i], (t$Free_rate[i]/100), 0.246575342*Remainb/90, (t$VIX[i]/100),0, 0)
  bb2 <- EuropeanOption("put", t$Close[i], t$Close[i],t$Div_rate_monthly[i], (t$Free_rate[i]/100), 0.246575342*Remainb/90, (t$VIX[i]/100),0, 0)


#  t$port4_absreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value)
#  t$port4_Perreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value) / (bb1$value+bb2$value)
  t$port4_Relreturn[i+1] = (aa1$value+aa2$value-bb1$value-bb2$value) / (bb1$value+bb2$value)*100000
}

t$port4_Perreturn <- t$port4_Relreturn/100000
```


#Dump first day NA return
```{r}
#t <- t[-1,]
```

x <- rep(NA, ncol(dat))
dat <- rbind(x, dat)


setwd("F:/Dropbox/[IAQF_Max]/R")
write_csv(t,"../Data/data.csv")

